\documentclass{article}

\usepackage{float}
\restylefloat{table}

\usepackage{booktabs}

\title{Team Contributions: Final\\\progname}

\author{\authname}

\date{}

\input{../Comments}
\input{../Common}

\begin{document}

\maketitle

This document summarizes the contributions of each team member for the final
demonstration and documentation.  The time period of interest is the time
between Rev 0 and the Final documentation; the contributions prior to Rev0 are
NOT included.

\section{Team Meeting Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 2 \\
Ruida Chen & 2 \\
Jiaming Li & 2 \\
Alvin Qian & 2 \\
Ammar Sharbat & 2 \\
\bottomrule
\end{tabular}
\end{table}

Explanation:
\begin{itemize}
    \item We don't meet that often as a team, rather we use Discord for communication generally, which is very hard to trace.
    \item All team meetings we have had to date have been added our Github Repo. Here are all of our \href{https://github.com/The-Crazy-Four-Games/Crazy_1-0s_Game/issues?q=is%3Aissue%20team%20meeting}{team meetings to date}.
\end{itemize}

\section{Supervisor/Stakeholder Meeting Attendance}

\noindent \textbf{Supervisor's Name: } Paul Rapoport; Email: rapoport@mcmaster.ca\\
\noindent \textbf{Other Stakeholders: } Card game players, web game players and other potential users of the game.

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 3 \\
Ruida Chen & 2 \\
Jiaming Li & 2 \\
Alvin Qian & 2 \\
Ammar Sharbat & 3 \\
\bottomrule
\end{tabular}
\end{table}

Explanation:
\begin{itemize}
    \item We had two supervisor meetings to follow up on our Rev0. See the 1st one \href{https://github.com/The-Crazy-Four-Games/Crazy_1-0s_Game/issues/257}{here} and the 2nd one \href{https://github.com/The-Crazy-Four-Games/Crazy_1-0s_Game/issues/263}{here}.
    \item All meetings with Professor Rapoport were initiated by teammate Ammar Sharbat, because he is the team liaison to the supervisor.
    \item Teammate Ammar met with stakeholders (card game players and family members) to try teaching them how to count in different number bases to figure out a solution to the Dozenal teaching problem. See the family meeting \href{https://github.com/The-Crazy-Four-Games/Crazy_1-0s_Game/issues/285}{here}, other meetings to be added.
\end{itemize}

\section{Lecture Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 1 \\
Ruida Chen & 1 \\
Jiaming Li & 1 \\
Alvin Qian & 1 \\
Ammar Sharbat & 1 \\
\bottomrule
\end{tabular}
\end{table}

The final lecture was not attended in person by any team members, but the lecture slides were read by all team members. See final lecture issue \href{https://github.com/The-Crazy-Four-Games/Crazy_1-0s_Game/issues/233}{here}.\\

\section{TA Document Discussion Attendance}

\noindent \textbf{TA's Name: } [Chris Schankula]

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meeting Attended}\\
\midrule
Total & 0\\
Ruida Chen & 0 \\
Jiaming Li & 0 \\
Alvin Qian & 0 \\
Ammar Sharbat & 0 \\
\bottomrule
\end{tabular}
\end{table}

Explanation:\\
No informal TA meetings occured between Rev0 and Rev1.\\

\section{Commits}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Commits} & \textbf{Percent}\\
\midrule
Total & 22 & 100\% \\
Ruida Chen & 4 & 18.18\% \\
Jiaming Li & 13 &59.09 \% \\
Ammar Sharbat & 1 & 4.5\% \\
Alvin Qian & 4 & 18.18\% \\
\bottomrule
\end{tabular}
\end{table}
\subsection{Explanation}
\begin{itemize}
    \item The commit counts above include all commits made to the \href{https://github.com/The-Crazy-Four-Games/Crazy\_1-0s\_Game/commits/main}{main branch} and \href{https://github.com/The-Crazy-Four-Games/Crazy\_1-0s\_Game/commits/test\_web}{test\_web branch} between Feb 3 to March 25. The commits were counted manually.
    \item \textbf{Note: Different teammates use different commit styles.} Some prefer batching changes into a few large commits after completing a section, while others commit incrementally. As a result, the number of commits does not necessarily correspond directly to workload or contribution size.
\end{itemize}

\section{Issue Tracker}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Authored (O+C)} & \textbf{Assigned (C only)}\\
\midrule
Ruida Chen& 17 & 20 \\
Jiaming Li & 17 & 16 \\
Ammar Sharbat & 8 & 10 \\
Alvin Qian & 5 & 8 \\
\bottomrule
\end{tabular}
\end{table}

\section{Team Charter Trigger Items}

The team has identified several triggers within the team charter to monitor collaboration and performance consistency:

\begin{itemize}
    \item \textbf{Commit Frequency:} Each member should contribute at least one meaningful commit per week.
    Falling below this threshold for two consecutive weeks triggers a discussion about workload balance.
    \item \textbf{Meeting Attendance:} Missing two consecutive team meetings without prior notice triggers a check-in with the member to identify scheduling or communication issues.
    \item \textbf{Branch Discipline:} All code changes must go through a pull request reviewed by at least one teammate.
    Direct commits to \texttt{main} are not allowed and will trigger an immediate process review.
    \item \textbf{Responsiveness:} Team members are expected to reply to key project communications (e.g., PR reviews or Slack updates) within 24 hours.
    Failure to respond repeatedly triggers a group discussion for reassigning responsibilities.
\end{itemize}

So far, no major trigger violations have occurred. The team has maintained consistent communication and review discipline.
If violations are observed in the future, the plan is to (1) hold a brief retrospective discussion,
(2) revise or clarify the trigger threshold if needed, and (3) document the agreed corrective action in the next meeting notes.


\section{Additional Productivity Metrics}

TBD.

\wss{If your team has additional metrics of productivity, please feel free to
add them to this report.}

\end{document}