\documentclass{article}

\usepackage{float}
\restylefloat{table}

\usepackage{pgfmath}

\usepackage{booktabs}

\title{Team Contributions: Crazy 1-0s Game \\ POC Demo}

\author{
    Team \#25, The Crazy Four \\[1ex]
    Ruida Chen \\
    Ammar Sharbat \\
    Alvin Qian \\
    Jiaming Li
}

\date{\today}

\input{../Comments}
\input{../Common}

\begin{document}

\maketitle

This document summarizes the contributions of each team member up to the POC
Demo.  The time period of interest is the time between the beginning of the term
and the POC demo.

\section{Demo Plans}

\subsection*{Overview}
The POC demo will be performed in-person and run locally from a group member's laptop. The goal is to demonstrate the core gameplay mechanics and an end-to-end 1v1 game flow.

\subsection*{Setup}
\begin{itemize}
	\item Start the local server (\texttt{Node.js} terminal server) on the presenter's machine.
	\item Use the hard-coded two-player configuration (no authentication for the POC).
	\item Open the game in a browser on the presenter machine.
\end{itemize}

\subsection*{Demo flow (approx. 5--7 minutes)}
\begin{enumerate}
	\item Brief introduction of demo objective (30s).
	\item Show initial game state: deck creation and hands dealt to both players.
	\item Two team members will control each player and demonstrate gameplay:
		\begin{itemize}
			\item Playing cards from a hand.
			\item Demonstrating matching logic (suit, rank, and add-to-10 rule).
			\item Demonstrating wildcard logic (changing the suit).
			\item Demonstrating drawing a card when no valid plays are available.
		\end{itemize}
	\item Drive the game to an endgame state and show the end condition.
	\item Conclude with limitations and next steps, then take questions.
\end{enumerate}

\subsection*{Notes}
\begin{itemize}
	\item No login/authentication is required for this POC demo.
	\item Will mention current limitations (hard-coded users, basic UI) and planned next steps.
\end{itemize}


\section{Team Meeting Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 3 \\
Ruida Chen & 3 \\
Jiaming Li & 3 \\
Alvin Qian & 3 \\
Ammar Sharbat & 3 \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Explanation}
\begin{itemize}
    \item Realistically, we have had very few team meetings. This is largely because of the packed schedules of 3 team members and also the fact that project management and communication through Discord has taken precedence over in person or virtual meetings.
    \item All team meetings have a corresponding GitHub issue with attendance, agendas and usually notes. To see our team meetings before POC, view links: \href{https://github.com/The-Crazy-Four-Games/Crazy\_1-0s\_Game/issues/214}{SRS meeting}, \href{https://github.com/The-Crazy-Four-Games/Crazy\_1-0s\_Game/issues/107}{Design Documentation: MG, MIS}, \href{https://github.com/The-Crazy-Four-Games/Crazy\_1-0s\_Game/issues/128}{POC Demo Prep}.
\end{itemize}

\section{Supervisor/Stakeholder Meeting Attendance}

\noindent \textbf{Supervisor and Key Stakeholder: } Paul Rapoport; Email: rapoport@mcmaster.ca

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 8 \\
Ruida Chen & 3 \\
Jiaming Li & 2 \\
Alvin Qian & 3 \\
Ammar Sharbat & 8 \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Explanation}
\begin{itemize}
    \item All supervisor meetings are on Github, see \href{https://github.com/The-Crazy-Four-Games/Crazy_1-0s_Game/issues?q=supervisor%20meeting%20sort%3Acreated-desc}{here}.
    \item While we created an issue for the POC Demo itself, it was not counted in tally above, as it is mandatory to attend.
    \item Teamate Ammar has the most inflated count for meetings, but this is because he was the lead on Game Design and project management (which was a focus of several 1-on-1 meetings with Supervisor Paul Rapoport).
    \item Teammate Ammar was also the only one to attend lectures after Week 1, and several meetings with supervisors took place after capstone lectures.
    \item Other teammates (Ruida, Jim and Alvin) have attended important meetings with Dr. Rapoport to update and discuss project progress and problems. They have done their part.
    \item Teammate Jiaming Li missed one \href{https://github.com/The-Crazy-Four-Games/Crazy_1-0s_Game/issues/43}{meeting} due to family reasons.
\end{itemize}

\section{Lecture + Tutorial Attendance\\    or  \\Lectures + Tutorials Read}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 13 \\
Ruida Chen & 13 \\
Jiaming Li & 13 \\
Alvin Qian & 7 \\
Ammar Sharbat & 11 \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Tutorials}\\
\midrule
Total & 3 \\
Ruida Chen & 3 \\
Jiaming Li & 2 \\
Alvin Qian & 1 \\
Ammar Sharbat & 2 \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Explanation}
\begin{itemize}
    \item Note: Both tallies are not entirely accurate. Teammate Alvin Qian has not checkmarked attendance/reading of classes, so the number listed may be higher.
    \item These are only the classes that were attended before our POC Demo (on November 26, 2026). Classes that happened after are not in this report.
    \item See all Lecture and Tutorial Issues for our project \href{https://github.com/The-Crazy-Four-Games/Crazy_1-0s_Game/issues?q=is%3Aissue%20lecture%20sort%3Acreated-desc&page=1}{here} to verify attendance/reading.
\end{itemize}

\section{TA Document Discussion Attendance}

\noindent \textbf{TA's Name: } [fill in this information]

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 4\\
Ruida Chen & 4 \\
Jiaming Li & 4 \\
Alvin Qian & 4 \\
Ammar Sharbat & 3 \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Explanation}
\begin{itemize}
    \item \textbf{Note: }Our team had a TA switch after the first document discussion (PS+Goals \& DevPlan), from TA Rashad to TA Chris. 
    \item TA Chris has been very helpful and provided great feedback on our deliverables.
    \item For the SRS Informal Discussion, TA Chris was not available after for two consecutive weeks for this because he was travelling. Also because our team didn't seek to schedule the meeting.
    \item Teammate Ammar Sharbat missed the TA document discussions (on VnVPlan) due to family reasons. 
\end{itemize}

\section{Commits}

Time Period : Beginning of Course - November 26 (POC Demo)

% Define commit counts (not printed)
% If there are any updates to your commit totals, please update the variables below with the correct number.
\pgfmathtruncatemacro{\cRuida}{47}
\pgfmathtruncatemacro{\cJiaming}{31}
\pgfmathtruncatemacro{\cAmmar}{35}
\pgfmathtruncatemacro{\cAlvin}{31}
\pgfmathtruncatemacro{\cTotal}{\cRuida+\cJiaming+\cAmmar+\cAlvin}

% Compute percentages (one decimal, not printed)
\pgfmathsetmacro{\pRuida}{100*\cRuida/\cTotal}
\pgfmathsetmacro{\pJiaming}{100*\cJiaming/\cTotal}
\pgfmathsetmacro{\pAmmar}{100*\cAmmar/\cTotal}
\pgfmathsetmacro{\pAlvin}{100*\cAlvin/\cTotal}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Commits} & \textbf{Percent}\\
\midrule
Total & \cTotal & 100\% \\
Ruida Chen & \cRuida & \pRuida\% \\
Jiaming Li & \cJiaming & \pJiaming\% \\
Ammar Sharbat & \cAmmar & \pAmmar\% \\
Alvin Qian & \cAlvin & \pAlvin\% \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Explanation}
\begin{itemize}
    \item The commit counts above include all commits made to the \href{https://github.com/The-Crazy-Four-Games/Crazy\_1-0s\_Game/commits/main}{main branch} until November 26, 2025 (our POC Demo). The commits were counted manually.
    \item \textbf{Note: Different teammates use different commit styles.} Some prefer batching changes into a few large commits after completing a section, while others commit incrementally. As a result, the number of commits does not necessarily correspond directly to workload or contribution size.
    \item Keep in mind, pull requests and merge / automated commits are included in these counts as well, especially for Teammate Ruida, Ammar and Alvin.
\end{itemize}


\section{Issue Tracker}

Time Period : Beginning of Course - November 26 (POC Demo)

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Authored (O+C)} & \textbf{Assigned (C only)}\\
\midrule
Ruida Chen & 21 & 46\\
Jiaming Li & 20 & 58\\
Alvin Qian & 2 & 39\\
Ammar Sharbat & 57 & 48\\
\bottomrule
\end{tabular}
\end{table}

\subsection{Explanation}
\begin{itemize}
    \item \textbf{Note: Future issues (work finished after the POC Demo) is NOT included in the issue counts and totals in the above table. Though, the tallying for issues for work that happened before the POC is a bit nuanced (see below reasons).}
    \item Many issues in our repo were created before our POC Demo but were \href{https://github.com/The-Crazy-Four-Games/Crazy\_1-0s\_Game/issues?q=is%3Aissue%20state%3Aclosed%20sort%3Acreated-desc%20POC}{closed long after}, either due to delay in resolution or due to being left open unintentionally.
    \item Similarly, many project tasks (e.g. deliverable work, lectures) were finished before our POC, but were \href{https://github.com/The-Crazy-Four-Games/Crazy\_1-0s\_Game/issues?q=is%3Aissue%20state%3Aclosed%20sort%3Acreated-desc%20lecture}{authored (and hence created) long after the POC}. They needed to be made for accurate tracking / traceability purposes, but the dates are not accurate to before our POC.
    \item In both of these cases, the mentioned issues were ignored from the tally above (for before POC Demo). The tally above is only concerned with authored (opened + closed) and assigned (closed) issues for project work or coursework (like lectures, deliverables) that happened \textbf{before our POC Demo}. Rest assured, our issue tracking and counting is very diligent and accurate.
    \item Teammate Alvin has the lowest issue tally among team members, but this is primarily because he focused more on deliverables and programming and less on issue tracking.
    \item You may notice that the assigned tally (181 total) is much higher than the authored tally (100 total). This is because many issues (like all lectures, and all meetings) were assigned to everyone, and not individually.
\end{itemize}

\section{CICD}

The project repository is hosted on GitHub and uses GitHub Actions for Continuous Integration and Continuous Deployment (CICD).
Each push or pull request triggers an automated workflow that performs the following tasks:

\begin{itemize}
    \item \textbf{Build and Lint:} The workflow installs all dependencies, compiles the code, and runs ESLint to enforce consistent formatting and syntax.
    \item \textbf{Unit Testing:} All Jest test suites are executed automatically. Code coverage reports are uploaded to Codecov.
    \item \textbf{Static Analysis:} CodeQL is run to detect potential vulnerabilities and logic errors.
    \item \textbf{Artifact Packaging:} For successful builds, the workflow produces a testable web or desktop artifact for internal review.
\end{itemize}

This setup ensures that any code merged into the \texttt{main} branch has passed validation for correctness, maintainability, and security.
By automating these checks, CICD reduces integration errors and accelerates the development feedback cycle.

\section{Team Charter Trigger Items}

The team has identified several triggers within the team charter to monitor collaboration and performance consistency:

\begin{itemize}
    \item \textbf{Commit Frequency:} Each member should contribute at least one meaningful commit per week.
    Falling below this threshold for two consecutive weeks triggers a discussion about workload balance.
    \item \textbf{Meeting Attendance:} Missing two consecutive team meetings without prior notice triggers a check-in with the member to identify scheduling or communication issues.
    \item \textbf{Branch Discipline:} All code changes must go through a pull request reviewed by at least one teammate.
    Direct commits to \texttt{main} are not allowed and will trigger an immediate process review.
    \item \textbf{Responsiveness:} Team members are expected to reply to key project communications (e.g., PR reviews or Slack updates) within 24 hours.
    Failure to respond repeatedly triggers a group discussion for reassigning responsibilities.
\end{itemize}

So far, no major trigger violations have occurred. The team has maintained consistent communication and review discipline.
If violations are observed in the future, the plan is to (1) hold a brief retrospective discussion,
(2) revise or clarify the trigger threshold if needed, and (3) document the agreed corrective action in the next meeting notes.


\section{Additional Productivity Metrics}

\wss{If your team has additional metrics of productivity, please feel free to
add them to this report.}

\end{document}