% THIS DOCUMENT IS FOLLOWS THE VOLERE TEMPLATE BY Suzanne Robertson and James Robertson
% ONLY THE SECTION HEADINGS ARE PROVIDED
%
% Initial draft from https://github.com/Dieblich/volere
%
% Risks are removed because they are covered by the Hazard Analysis
\documentclass[12pt]{article}

\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{hyperref}
\usepackage{graphicx}
\hypersetup{
    bookmarks=true,         % show bookmarks bar?
      colorlinks=true,      % false: boxed links; true: colored links
    linkcolor=red,          % color of internal links (change box color with linkbordercolor)
    citecolor=green,        % color of links to bibliography
    filecolor=magenta,      % color of file links
    urlcolor=cyan           % color of external links
}

\newcommand{\lips}{\textit{Insert your content here.}}

\input{../Comments}
\input{../Common}

\begin{document}

\title{Software Requirements Specification for \progname: subtitle describing software}
\author{
    Team \#25, The Crazy Four \\[1ex]
    Ruida Chen \\
    Ammar Sharbat \\
    Alvin Qian \\
    Jiaming Li
}
\date{30.09.2025}
    
\maketitle

~\newpage

\pagenumbering{roman}

\tableofcontents

~\newpage

\section*{Revision History}

\begin{table}[hp]
    \caption{Revision History} \label{TblRevisionHistory}
    \begin{tabularx}{\textwidth}{llX}
        \toprule
        \textbf{Date} & \textbf{Developer(s)} & \textbf{Change}\\
        \midrule
        9.29 & Jiaming Li & 1 - Purpose of the Project\\
        9.30 & Ruida Chen & Section 3, 10 ,11,  12\\
        9.30 & Jiaming Li & 8 - Scope of the Product\\
        9.30 & Jiaming Li & 9 - Functional Requirements\\
        9.30 & Alvin Qian & Section 4,6,7\\
        10.1 & Alvin Qian & Section 14,16\\
        10.9 & Ruida Chen & Section 20,21,22\\
        10.9 & Jiaming Li & Section 17,18,19\\
        10.9 & Alvin Qian & Appendix and Reflection\\
        10.12 & Ammar Sharbat & Section 1.1, 2, 5, 13, 15, 18\\
        10.13 & Ammar Sharbat & Section 18, 19, 25\\
        \bottomrule
    \end{tabularx}
\end{table}

~\\

~\newpage
\section{Purpose of the Project}
\subsection{User Business}
The purpose is to study, evaluate and facilitate opportunities for gamification in supporting mathematical learning. Our team wants to determine whether concepts in numerical arithmetic (such as base conversions, or divisibility in Dozenal) can be effectively taught through play.\\\\
We aim to accomplish the aformentioned by designing and implementing an educational card game based on the traditional \textit{Crazy 8s} rule set, but with the following differences and additions:
\begin{itemize}
    \item Switching the wild card from ``8'' to ``10'' to improve awareness of number system orders (i.e. 10 in base-10 is a Decimal is 10 in base-12 is a Dozenal).
    \item Incorporating counting within the game, to improve understanding of number bases and basic arithmetic.
    \item Integrating the \textbf{Dozenal (base-12) number system} using a special Dozenal deck of cards. We also want to add other potential number bases (e.g. Octal, Hexadecimal, etc).
\end{itemize}

\subsection{Goals of the Project}
The goals of this project are:
\begin{itemize}
    \item Educational Integration: Seamlessly incorporate Dozenal concepts (numerical symbols, factorization, arithmetic) into the gameplay, ensuring that players learn by playing without requiring formal prior knowledge.
    \item Gameplay Design: Deliver a working digital version of this variant of \textit{Crazy 8s} that is intuitive, responsive, and enjoyable, while maintaining the familiar flow of the original game and introducing Dozenal-specific mechanics.
    \item Accessibility: Create a user-friendly interface that lowers the barrier to learning, accessible for casual users while offering depth for learners who want to explore Dozenal further.
    \item Testability: Implement robust testing strategies to ensure correctness of game logic, Dozenal calculations, and user interactions.
    \item Measuring Educational Impact (Stretch Goal): Assessing impact by collecting user data through user engagement, playtesting, progress monitoring and player feedback collection.
    \item Scalability (Stretch Goal): Explore the potential for extending the system to other educational card or board games, and investigate how different number bases can be taught through similar game mechanics.
\end{itemize}

\section{Stakeholders}

\subsection{Client}
\begin{itemize}
  \item \textbf{Supervisor} Dr. Spencer Smith - primary sponsor of the deliverable; approves acceptance criteria for academic evaluation and EXPO demonstration.
  \item \textbf{Supervisor:} Dr. Paul Rapoport — academic acceptance authority and milestone reviewer.
\end{itemize}

\subsection{Customer}
\begin{itemize}
  \item \textbf{Course Instructor / Teaching Staff:} Consumer of the deliverable for grading and course outcomes.
  \item \textbf{End-users (primary customer persona):} Educators and students who may adopt the game as a learning aid; they decide whether the product fits classroom or self-study needs.
\end{itemize}

\subsection{Other Stakeholders}
\begin{itemize}
  \item \textbf{Subject Matter Experts:} Dozenal advocates/educators consulted for correctness of dozenal content.
  \item \textbf{Usability / Accessibility Experts:} Provide guidance to meet WCAG guidelines.
  \item \textbf{IT / Hosting Providers:} Maintain hosting infrastructure and CI/CD.
  \item \textbf{Testers / Demonstration Audience:} Provide feedback during PoC and demos.
\end{itemize}

\subsection{Hands-On Users of the Product}
\begin{itemize}
  \item \textbf{Casual Learners (novice):} Students or hobbyists with little/no dozenal experience. Low technical skill; require strong onboarding and hints.
  \item \textbf{Educators (journeyman):} Teachers who use the game in lessons; expect configurable sessions and exportable results.
  \item \textbf{Capstone Evaluators / Demo Attendees (master/journeyman):} Technical audience who will assess correctness, stability, and educational value.
\end{itemize}

\subsection{Personas}
\begin{itemize}
  \item \textbf{Maya (16, Student)}: Low dozenal familiarity; wants a short tutorial and visual hints to learn while playing.
  \item \textbf{Prof. Singh (45, Educator)}: Wants quick setup for classroom demo, configurable rules, and exportable session results.
  \item \textbf{Jordan (21, Competitive Hobbyist)}: Interested in multiplayer fairness and replay logs; tolerates brief tutorials.
\end{itemize}

\subsection{Priorities Assigned to Users}
\begin{itemize}
  \item \textbf{Key users:} Educators and students (primary product purpose is educational adoption).
  \item \textbf{Secondary users:} Demonstration evaluators, hobbyists.
  \item \textbf{Low priority:} Anonymous spectators and infrequent guest users.
\end{itemize}

\subsection{User Participation}
\begin{itemize}
  \item \textbf{Educator involvement:} Review of tutorial content and alignment with learning objectives (estimated 2--4 hours over term).
  \item \textbf{Student testing:} Playtest sessions (estimated 3--5 sessions of 20--30 minutes) to validate usability and learning uptake.
  \item \textbf{Developer/Testers:} Ongoing involvement in unit/integration test creation and bug triage.
\end{itemize}

\subsection{Maintenance Users and Service Technicians}
\begin{itemize}
  \item \textbf{DevOps / Maintainers:} Responsible for deployment, backups, and monitoring. Require documentation on deployment scripts and DB snapshot procedures.
  \item \textbf{Support Contact (team liaison):} Handles escalations and coordinates fixes with team members.
\end{itemize}

\subsubsection*{Fit criterion}
Stakeholder list and contact/role assignments exist in the project README and team Kanban; at least one named representative for each stakeholder category is recorded. Evidence: README / Team Roles section and meeting minutes indicating stakeholder reviews.


\section{Mandated Constraints}
\subsection{Solution Constraints}
	\begin{itemize}
		\item All source code must be managed using Github, with frequent commits and version control.
		\item The system must be developed using React for frontend and Node.js for backend.
	\end{itemize}
\subsection{Implementation Environment of the Current System}
\begin{itemize}
		\item The backend must operate on Node.js (LTS version, e.g., 18+) with a relational database such as PostgreSQL or MySQL.
		\item The application must be deployable on modern web browsers (Chrome, Firefox, Edge)
	\end{itemize}
\subsection{Partner or Collaborative Applications}
	\begin{itemize}
		\item The team must use GitHub for code collaboration and issue tracking.
		\item  Discord are required for real-time communication and coordination.
	\end{itemize}
\subsection{Off-the-Shelf Software}
	\begin{itemize}
		\item The system must rely primarily on open-source libraries.
		\item Proprietary software must not be required for end users to run the application.
	\end{itemize}
\subsection{Anticipated Workplace Environment}
	\begin{itemize}
		\item End users are expected to interact with the application primarily on web browsers.
	\end{itemize}
\subsection{Schedule Constraints}
	\begin{itemize}
		\item The project must be completed within the academic deadline.
		\item Progress reports and milestone check-ins with the TA are mandatory.
	\end{itemize}
\subsection{Budget Constraints}
	\begin{itemize}
		\item Total financial budget is under 500 Canadian Dollars.
		\item Open source and free tools are primary to be used.
	\end{itemize}
\subsection{Enterprise Constraints}
	\begin{itemize}
		\item The project must comply with academic integrity and university policies.
		\item Data collection and storage must follow privacy, security, and ethical guidelines.
	\end{itemize}

\section{Naming Conventions and Terminology}
\subsection{Glossary of All Terms, Including Acronyms, Used by Stakeholders
involved in the Project}

\begin{itemize}
    \item \textbf{Base-10 (Decimal)}: The standard numerical system using ten digits (0--9), commonly used in arithmetic and everyday calculations.
    \item \textbf{Base-12 (Dozenal)}: A numerical system using twelve digits (0--9, \reflectbox{2}, \reflectbox{3}), where \reflectbox{2} represents 10 and \reflectbox{3} represents 11 in decimal. Has divisibility advantages (divisors: 2, 3, 4, 6).
    \item \textbf{Base-8 (Octal)}: A numerical system using eight digits (0--7). Each octal digit represents three binary digits (bits). Commonly used in computing and digital systems due to easy conversion with binary.
    \item \textbf{Base-16 (Hexadecimal)}: A numerical system using sixteen digits (0--9, A--F), where A through F represent decimal values 10 to 15. Widely used in programming and computer memory addressing for its compact binary representation.
    \item \textbf{Crazy Eights}: A classic card game where players match cards by suit or rank, with the ``8'' card acting as a wild card allowing the player to declare a new suit.
    \item \textbf{MVP}: Minimum Viable Product, the initial version of the Crazy Eights software with core functionality, including two-player gameplay, classic rules, and dozenal scoring.
    \item \textbf{Functional Goals}: Features and behaviors the software must implement, such as gameplay mechanics and dozenal score display.
    \item \textbf{Non-functional Goals}: Quality attributes of the software, such as usability, performance, and stability.
    \item \textbf{Stretch Goals}: Optional features or enhancements, such as multiplayer support or advanced dozenal rule variants, to be implemented if time permits.
    \item \textbf{GitHub}: The platform used for version control, issue tracking, and Kanban board management.
    \item \textbf{Discord}: The communication platform for team coordination, quick updates, and voice meetings.
    \item \textbf{Kanban Board}: A project management tool in GitHub Projects, divided into stages (Backlog, In Progress, Review, Done) to track tasks.
    \item \textbf{CI/CD}: Continuous Integration/Continuous Deployment, an automated process for testing and deploying code changes.
    \item \textbf{SRS}: Software Requirements Specification, this document outlining the requirements for the Crazy Eights project.
    \item \textbf{PoC}: Proof of Concept, a prototype demonstrating core gameplay mechanics to validate feasibility.
    \item \textbf{UI}: User Interface, the visual and interactive components of the software, such as the game board and score display.
\end{itemize}

\section{Relevant Facts and Assumptions}

\subsection{Relevant Facts}
\begin{itemize}
  \item \textbf{Prevalence of decimal:} Users are overwhelmingly familiar with base-10; dozenal notation is novel for most.
  \item \textbf{Educational effectiveness:} Game-based learning improves numeracy engagement (backed by pedagogical literature).
  \item \textbf{Resource constraints:} Project budget is capped at 500 CAD and timeline is an academic term.
  \item \textbf{Technology stack:} Planned stack is React (frontend), Node.js (backend), PostgreSQL (data).
  \item \textbf{Browser target:} Modern desktop browsers (Chrome, Firefox, Edge) are the primary runtime environment.
\end{itemize}

\subsection{Business Rules}
\begin{itemize}
  \item \textbf{Scoring rule:} Round score equals sum of opponents' remaining card values (displayed in both decimal and dozenal).
  \item \textbf{Account rule:} Registered usernames must be unique; guest mode creates impermanent sessions.
  \item \textbf{Open-source rule:} All deliverables must use appropriately licensed assets; avoid proprietary-only dependencies.
\end{itemize}

\subsection{Assumptions}
\begin{itemize}
  \item \textbf{Connectivity:} Players typically have a stable internet connection for multiplayer sessions.
  \item \textbf{Device:} Primary devices are desktop/laptop; mobile support is a stretch-goal.
  \item \textbf{Play familiarity:} Players understand basic card game mechanics (matching suit or rank).
  \item \textbf{Team availability:} Team members will perform peer review before merges as per Development Plan.
  \item \textbf{Third-party components:} Standard open-source libraries (React, Socket.io, PG client) will be available and compatible.
\end{itemize}

\section{The Scope of the Work}
\subsection{The Current Situation}

The current numerical system used around the world is predominantly decimal (base-10). This system, while widely adopted, has limitations in representing fractions cleanly, as its prime factors (2 and 5) result in recurring decimals for simple ratios 1/3 or 1/6. On the other hand, the dozenal (base-12) system, with divisors 2, 3, 4, and 6, offers a more intuitive and concise fraction representations, historically used in trade and measurement systems (e.g., dozens, hours). However, dozenal is underutilized in education and practice, leaving students, educators, and professionals reliant on decimal despite its inefficiencies for certain calculations. There is no current fun and engaging way to demonstrate the practical advantages of dozenal, such as a card game like Crazy Eights, to promote its adoption.

\subsection{The Context of the Work}

The project focuses on the software implementation of the Crazy Eights card game that incorporates dozenal (base-12) scoring and display to highlight the benefits of the dozenal system. The context includes:

\begin{itemize}
    \item \textbf{Educational Context}: The project will simplify mathematical understanding for the user by showing dozenal's advantages in a familiar and fun game format.
    \item \textbf{Technical Context}: The software will be developed using a modern tech stack for web applications (JavaScript, TypeScript, Node.js, React, PostgreSQL) and use GitHub CI/CD pipelines for version control and testing.
    \item \textbf{Stakeholder Context}: Key stakeholders include students, educators, mathematicians, computer scientists, and the general public, all of whom could benefit from clearer fraction representations and easier mental arithmetic.
\end{itemize}

\subsection{Work Partitioning}

The workload is divided into the following major phases, aligned with the development plan:

\begin{enumerate}
    \item \textbf{Problem Definition and Planning (Weeks 3--4)}: Draft problem statement, development plan, and initial proof of concept (PoC) to establish scope and feasibility.
    \item \textbf{Requirements and Hazard Analysis (Week 6)}: Develop the SRS and identify potential risks and mitigation strategies.
    \item \textbf{Verification and Validation Planning (Week 8)}: Define testing strategies to ensure the software meets functional and non-functional requirements.
    \item \textbf{System Design (Weeks 10--16)}: Create and refine architecture diagrams, decompose the system into modules (frontend, backend, database, API), and document extensibility.
    \item \textbf{Implementation and Testing (Weeks 11--19)}: Develop the MVP (two-player game with classic rules and dozenal scoring), conduct unit and integration testing, and prepare for demonstrations.
    \item \textbf{Demonstrations and Refinement (Weeks 19--24)}: Conduct Revision 0 and final demonstrations, incorporating feedback to improve functionality and performance.
    \item \textbf{Final Documentation and EXPO (Week 26)}: Finalize documentation and present a polished product at the EXPO.
\end{enumerate}

Each task is tracked via GitHub Issues and the Kanban board, with responsibilities assigned to team members based on rotating roles (developer, reviewer, meeting chair, note-taker).

\subsection{Specifying a Business Use Case (BUC)}

\textbf{BUC: Play a Game of Crazy Eights with Dozenal Scoring}

\begin{itemize}
    \item \textbf{Actors}: Two players, the software system.
    \item \textbf{Trigger}: A player creates a new game session using the UI.
    \item \textbf{Description}: Two players take turns matching cards by suit or rank, with the ``10'' card acting as a wild card that allows the player to declare a new suit. If no valid move can be made, the player draws from the stock pile. The game ends when one player discards all their cards, and the score is calculated and displayed in dozenal notation.
    \item \textbf{Preconditions}: The user is logged in. The software is running on a web interface, with a functional UI displaying the hand, discard pile, stock pile, and score tracker.
    \item \textbf{Postconditions}: The game concludes with a winner, points are displayed in dozenal and must be counted by the users to see the final score. The user can log Off or start a new game.
    \item \textbf{Basic Flow}:
    \begin{enumerate}
        \item The system deals cards to both players and initializes the discard pile with a starter card.
        \item Players take turns, selecting a card to play (matching suit or rank) or drawing from the stock pile.
        \item If an ``10'' is played, the player selects a new suit via the UI.
        \item The system checks moves and gives immediate feedback for invalid moves.
        \item The game keeps going until one player has no cards left, triggering user score counting and calculation challenge in dozenal.
        \item The system displays the final score.
    \end{enumerate}
    \item \textbf{Exceptions}:
    \begin{itemize}
        \item Invalid move attempted: The system highlights the error and prompts the player to select a valid card or draw.
        \item Stock pile exhausted: The system reshuffles the discard pile to replenish the stock pile.
    \end{itemize}
    \item \textbf{Assumptions}: Players are familiar with basic card game mechanics and the system supports a stable internet connection for play.
\end{itemize}

\section{Business Data Model and Data Dictionary}
\subsection{Business Data Model}

These are the key entities and relationships involved in the Crazy Eights game with dozenal scoring.

\begin{itemize}
    \item \textbf{Entities}:
    \begin{itemize}
        \item \textbf{Player}: Represents a game participant, holding a hand of cards and a score.
        \item \textbf{Card}: Represents a single playing card with a suit and rank.
        \item \textbf{Deck}: A collection of cards, divided into the stock pile and discard pile.
        \item \textbf{Game Session}: Tracks the state of a single game, including players, current turn, discard pile, and scores.
        \item \textbf{Score}: Tracks points in dozenal notation, calculated based on game rules.
    \end{itemize}
    \item \textbf{Relationships}:
    \begin{itemize}
        \item A \textbf{Game Session} has 2 \textbf{Players} (MVP) or 2--4 \textbf{Players} (stretch goal).
        \item Each \textbf{Player} has a \textbf{Hand} (subset of \textbf{Cards}).
        \item A \textbf{Deck} consists of 52 \textbf{Cards}, split into \textbf{Stock Pile} and \textbf{Discard Pile}.
        \item A \textbf{Game Session} produces a \textbf{Score} for each \textbf{Player} in dozenal notation.
        \item A \textbf{Card} played in a \textbf{Game Session} affects the \textbf{Discard Pile} and may trigger a suit change (if a ``10'').
    \end{itemize}
\end{itemize}

\subsection{Data Dictionary}

\begin{itemize}
    \item \textbf{Player}:
    \begin{itemize}
        \item \textbf{ID}: Unique identifier for a player (integer).
        \item \textbf{Name}: Display name for the player (string).
        \item \textbf{Hand}: List of cards held by the player (array of Card objects).
        \item \textbf{Score}: Player's cumulative score in dozenal notation (string, such as ``1\reflectbox{2}'' for 22 in decimal).
    \end{itemize}
    \item \textbf{Card}:
    \begin{itemize}
        \item \textbf{Suit}: One of four suits (Hearts, Diamonds, Clubs, Spades) (string).
        \item \textbf{Rank}: Card value (2--10, J, Q, K, A) (string).
        \item \textbf{IsWild}: Boolean indicating if the card is an ``10'' (true/false).
    \end{itemize}
    \item \textbf{Deck}:
    \begin{itemize}
        \item \textbf{Stock Pile}: List of cards available for drawing (array of Card objects).
        \item \textbf{Discard Pile}: List of played cards (array of Card objects).
    \end{itemize}
    \item \textbf{Game Session}:
    \begin{itemize}
        \item \textbf{Session ID}: Unique identifier for the game session (string).
        \item \textbf{Current Turn}: ID of the player whose turn it is (integer).
        \item \textbf{Status}: Game state (Active, Completed) (string).
        \item \textbf{Starter Card}: The first card in the discard pile (Card object).
        \item \textbf{Last Played Suit}: The active suit after an ``10'' is played (string).
    \end{itemize}
    \item \textbf{Score}:
    \begin{itemize}
        \item \textbf{Player ID}: Links to the player (integer).
        \item \textbf{Dozenal Value}: Score in base-12 notation (string, such as ``14'' for 16 in decimal).
        \item \textbf{Calculation Method}: Rules for scoring (sum of remaining cards in the opponents hands) (string).
    \end{itemize}
\end{itemize}


\section{The Scope of the Product}

\subsection{Product Boundary}
The product to be developed is a digital card game application based on the traditional \textit{Crazy 8s} rules, modified to integrate the \textbf{Dozenal (base-12) number system}.
The system boundary includes:
\begin{itemize}
    \item A game engine that supports core Crazy 8s mechanics (drawing, discarding, turn-taking, winning conditions).
    \item Adaptations of rules, card values, and scoring to incorporate Dozenal arithmetic and representations.
    \item A user interface allowing players to interact with the game (play cards, view scores, receive feedback).
    \item Educational prompts or visual aids to help players understand Dozenal concepts.
\end{itemize}
External systems not included in the boundary are: general learning platforms, multiplayer servers beyond basic peer-to-peer/local play, and integrations with unrelated educational tools.

\subsection{Product Use Case Table}
The following table summarizes the primary product use cases (PUCs):

\begin{tabularx}{\textwidth}{|l|X|}
    \hline
    \textbf{PUC \#} & \textbf{Description} \\
    \hline
    PUC-1 & Player logs into the system or creates a new account to enable personalized features and multiplayer access. \\
    \hline
    PUC-2 & Player views their personal profile, including gameplay history, win/loss record, and achievements. \\
    \hline
    PUC-3 & Player starts a new Crazy 8s game with Dozenal-enabled deck. \\
    \hline
    PUC-4 & Player takes a turn by drawing or discarding a card. \\
    \hline
    PUC-5 & System validates whether the played card is legal (same suit, same Dozenal value, or sum = 12). \\
    \hline
    PUC-6 & Player views scores and progress, displayed in both decimal and Dozenal. \\
    \hline
    PUC-7 & System provides hints or explanations to support Dozenal learning. \\
    \hline
    PUC-8 & Game ends when a player wins; final scores are calculated and displayed. \\
    \hline
\end{tabularx}

\subsection{Individual Product Use Cases (PUCs)}

\noindent\textbf{UC1: Player Login}
\begin{enumerate}
    \item Player opens the game application and selects ``Login'' or ``Create Account''.
    \item The system prompts the player to enter credentials (username and password) or choose guest mode.
    \item The system validates login information against the stored database.
    \item If credentials are valid, the player is granted access to personalized data (game progress, scores, and settings).
    \item If the player selects guest mode, a temporary profile is generated for the session.
    \item The system displays the main menu or lobby after login.
\end{enumerate}

\noindent\textbf{UC2: See Player Profile}
\begin{enumerate}
    \item The player selects ``View Profile'' from the main menu.
    \item The system retrieves player data (username, past game records, win/loss ratio, and achievements) from the database.
    \item The system displays profile information on screen.
    \item If the player is logged in as a guest, the system displays a message such as ``Profile unavailable for guest mode''.
    \item The player may choose to return to the main menu or edit available settings (if logged in).
\end{enumerate}


\noindent\textbf{UC3: Start a New Game}
\begin{enumerate}
    \item Player opens the application and selects ``New Game''.
    \item The system initializes a Dozenal-enabled deck (0--B, 10).
    \item The system shuffles the deck.
    \item The system deals cards to each player.
    \item The game state is displayed on the interface.
\end{enumerate}

\noindent\textbf{UC4: Take a Turn}
\begin{enumerate}
    \item The system indicates that it is the player’s turn.
    \item The player chooses either to play a card or to draw from the deck.
    \item If the player chooses a card, the system goes through \textbf{UC5} to check its validity against the discard pile.
    \item If valid, the card is placed onto the discard pile.
    \item If invalid, the system notifies the player and the card remains in the hand.
    \item If the player chooses to draw, the system gives one card from the deck to the player.
\end{enumerate}

\noindent\textbf{UC5: Validate Move}
\begin{enumerate}
    \item The player selects a card to play.
    \item The system retrieves the top card from the discard pile.
    \item The system checks if the move is legal under Dozenal rules:
    \begin{enumerate}
        \item same suit, or
        \item same Dozenal value, or
        \item sum of the two values equals 12 (base-12).
    \end{enumerate}
    \item If the move is legal, the system accepts the card and updates the discard pile.
    \item If not, the system rejects the move and notifies the player.
\end{enumerate}

\noindent\textbf{UC6: View Scores}
\begin{enumerate}
    \item A round ends or the player requests to view scores.
    \item The system calculates points for each player.
    \item The system converts the scores into both decimal and Dozenal.
    \item The system displays the results on screen.
\end{enumerate}

\noindent\textbf{UC7: Provide Hints}
\begin{enumerate}
    \item The player hovers over or selects a card.
    \item The system analyzes the current game state.
    \item The system provides a hint (e.g., ``This card is valid because its sum with the top card equals 12 (base-12).'').
    \item The hint is displayed as text or a visual highlight.
\end{enumerate}

\noindent\textbf{UC8: End Game}
\begin{enumerate}
    \item A player discards their last card.
    \item The system checks if the game-ending condition is satisfied.
    \item If satisfied, the system declares the winner.
    \item The system calculates final scores in both decimal and Dozenal.
    \item The results are displayed on the final game screen.
\end{enumerate}



\section{Functional Requirements}

\subsection{Game Manager}

\begin{enumerate}
    \item \textbf{Start new game:} Game manager shall allow the player to start a new Crazy 8s game with a Dozenal-enabled deck. (FR-1) \\
    \textbf{Rationale:} Players need a way to initialize the game state; starting a new game is the foundation for all other gameplay functions.

    \item \textbf{Turn management:} Game manager shall manage player turns, ensuring that each player either discards a valid card or draws a card. (FR-2) \\
    \textbf{Rationale:} Turn-taking enforces fairness and ensures game flow consistency.

    \item \textbf{Rule validation:} Game manager shall validate that each played card is legal under Dozenal rules. A valid move is defined as either: (a) same suit as the previous card, (b) same Dozenal value as the previous card, or (c) the sum of the two card values equals 12 in Dozenal. (FR-3) \\
    \textbf{Rationale:} Prevents illegal moves, guarantees consistency, and introduces the core educational mechanic of Dozenal arithmetic.

    \item \textbf{Special cards:} Game manager shall implement special card effects (e.g., 10s are wild) while supporting extensions with Dozenal-specific effects. (FR-4) \\
    \textbf{Rationale:} Special cards increase engagement and add flexibility in teaching Dozenal-based rules.

    \item \textbf{End of game:} Game manager shall determine when the game ends (e.g., when a player runs out of cards) and declare the winner. (FR-5) \\
    \textbf{Rationale:} A clear end condition is required for meaningful gameplay and reinforcement of learning objectives.
\end{enumerate}


\subsection{Score Manager}

\begin{enumerate}
    \item \textbf{Calculate score:} Score manager shall calculate points for each round in both decimal and Dozenal. (FR-6) \\
    \textbf{Rationale:} Displaying scores in both systems reinforces learning by encouraging comparison between familiar decimal and new Dozenal formats.

    \item \textbf{Display score:} Score manager shall display both decimal and Dozenal results on the user interface. (FR-7) \\
    \textbf{Rationale:} Visual feedback supports player understanding and helps users internalize Dozenal representations.
\end{enumerate}


\subsection{Education Support}

\begin{enumerate}
    \item \textbf{Hints:} System shall provide hints or explanations when a player performs an action involving Dozenal arithmetic. (FR-8) \\
    \textbf{Rationale:} On-demand guidance lowers the learning curve and supports players with varying levels of familiarity.

    \item \textbf{Highlight valid moves:} System shall visually highlight valid moves based on Dozenal rules. (FR-9) \\
    \textbf{Rationale:} Reduces frustration, ensures players stay engaged, and reinforces Dozenal rules through visual learning.
\end{enumerate}

\subsection{Login Manager}
\begin{enumerate}
    \item \textbf{Account creation:} The system shall allow players to create a new account with a unique username and password. (FR-10)
    \item \textbf{Login/Logout:} The system shall allow players to log in and log out at any time without losing progress. (FR-11)
    \item \textbf{Guest mode:} The system shall allow players to start a temporary session without login. (FR-12)
    \item \textbf{Credential validation:} The system shall validate player credentials against stored records before granting access. (FR-13)
    \item \textbf{Rationale:} Ensures users can have persistent profiles for tracking progress and enables multiplayer authentication.
\end{enumerate}

\subsection{Data Manager}
\begin{enumerate}
    \item \textbf{Data storage:} The system shall securely store user data, including usernames, game history, and Dozenal scores. (FR-14)
    \item \textbf{Data retrieval:} The system shall allow retrieval of stored user data when logging in or viewing profiles. (FR-15)
    \item \textbf{Data update:} The system shall update stored data after each game or when profile information changes. (FR-16)
    \item \textbf{Data deletion:} The system shall allow players to delete their data permanently upon request. (FR-17)
    \item \textbf{Rationale:} Supports persistent user experience, analytics, and compliance with data privacy expectations.
\end{enumerate}

\section{Look and Feel Requirements}
\subsection{Appearance Requirements}
	\begin{itemize}
		\item \textbf{Layout}: The user interface must have a clean and minimalistic layout, ensuring readability and ease of navigation.
		\item \textbf{Responsiveness}: The system must be responsive, adapting automatically to different screen sizes.
		\item \textbf{Visual Hierarchy}: Key elements such as active player indicators, playable cards, and turn timers must be visually distinguishable using contrast, color, or animation.
		\item \textbf{Color Palette}: The color scheme should promote clarity and engagement.
	\end{itemize}
\subsection{Style Requirements}
	\begin{itemize}
		\item \textbf{Consistency}: The application must follow a unified design language, maintaining consistent typography, iconography, and button styles across all screens.
		\item \textbf{Animations}: Smooth 2-D animations should be implemented for card movements, dealing, and discarding actions. These animations should be realistic but not distracting, maintaining short transition times. When a wild card is played, a distinct animation and color shift should visually emphasize its effect while maintaining overall style consistency.
		\item \textbf{In-Game Hints}: Hints should appear contextually (e.g., glowing borders, pulsing icons) rather than as intrusive pop-ups. They should guide the player without interrupting the flow of the game.
		
	\end{itemize}

\section{Usability and Humanity Requirements}
\subsection{Ease of Use Requirements}
	\begin{itemize}
		\item \textbf{Simplicity}: The interface must minimize the number of steps needed to perform core tasks.
		\item Data collection and storage must follow privacy, security, and ethical guidelines.
	\end{itemize}
\subsection{Personalization and Internationalization Requirements}
	\begin{itemize}
		\item \textbf{Language Options}: The system must support at least English and one additional language for international users.
	\end{itemize}
\subsection{Learning Requirements}
	\begin{itemize}
		\item \textbf{Onboarding}A short interactive tutorial must explain the rules of the game and how counting in different bases works.
	\end{itemize}
\subsection{Understandability and Politeness Requirements}
	\begin{itemize}
		\item \textbf{Friendly Wording}: Prompts like “Invalid Move” must be displayed as polite guidance.
		\item \textbf{Clear Instructions}: Rules and base-conversion explanations must be phrased in simple and non-technical terms.
	\end{itemize}
\subsection{Accessibility Requirements}
	\begin{itemize}
		\item\textbf{Keyboard Support}: All main actions must be accessible via keyboard shortcuts
	\end{itemize}

\section{Performance Requirements}
\subsection{Speed and Latency Requirements}
	\begin{itemize}
		\item\textbf{Low latency}: Game actions must update across all players’ screens within 300 ms.
		\item \textbf{Fast loading}: The game lobby and first match must load within 5 seconds on a stable internet connection.
	\end{itemize}

\subsection{Safety-Critical Requirements}
	\begin{itemize}
		\item\textbf{Cheat Prevention}: The system must prevent unauthorized manipulation (e.g., directly altering game state through client-side tools).
		\item \textbf{Data Integrity}: No game state (e.g. deck composition, player hand) should be lost or corrupted due to refresh or reconnect.
	\end{itemize}

\subsection{Precision or Accuracy Requirements}
	\begin{itemize}
		\item\textbf{Card Rules}: Card-matching and counting rules must be enforced with 100\% accuracy according to the chosen numeral base.
	\end{itemize}

\subsection{Robustness or Fault-Tolerance Requirements}
	\begin{itemize}
		\item\textbf{Reconnection}: If a player disconnects, they must be able to rejoin within 30 seconds without losing progress.
	\end{itemize}

\subsection{Capacity Requirements}
	\begin{itemize}
		\item\textbf{Concurrent Players}: The system must support at least 200 concurrent users during testing.
	\end{itemize}

\subsection{Scalability or Extensibility Requirements}
	\begin{itemize}
		\item\textbf{Game Modes}: The system must allow for adding new rule variations (e.g., different numeral bases or wild card effects) with minimal code changes.
		\item \textbf{Server Scaling}: The backend must be deployable in a scalable environment (e.g., Docker, cloud hosting) to handle larger user bases.
	\end{itemize}

\subsection{Longevity Requirements}
	\begin{itemize}
		\item\textbf{Maintainability}: The codebase must be modular and documented, so future developers can update rules easily.
	\end{itemize}

\section{Operational and Environmental Requirements}

\subsection{Expected Physical Environment}
\begin{itemize}
  \item The product will be used on desktop/laptop computers in classrooms, homes, and demo booths under normal indoor lighting and noise conditions.
  \item Typical input devices: keyboard and mouse; mouse will be primary input device; keyboard interaction considered a stretch goal.
  \item No special physical environment (temperature, humidity, dust) requirements are expected.
\end{itemize}

\subsection{Requirements for Interfacing with Adjacent Systems}
\begin{itemize}
  \item \textbf{Authentication API:} Integrate with a simple backend-auth service (REST endpoints) for account creation and login.
  \item \textbf{Telemetry / Analytics (optional):} Provide an HTTP endpoint to export anonymized session metrics for research (GDPR-compliant).
  \item \textbf{Hosting / CI:} Integration with GitHub Actions for tests and deploy; target hosting platform must accept standard Docker containers or static web app hosting.
\end{itemize}

\subsection{Productization Requirements}
\begin{itemize}
  \item Distribution as a web application (hosted) and a developer-local deployment (Docker-compose) for evaluation.
  \item Installation for in-person demos should require at most three documented steps (clone, install, run).
\end{itemize}

\subsection{Release Requirements}
\begin{itemize}
  \item Release cadence: a demonstration-ready milestone (PoC) and a final-revision release for EXPO.
  \item Releases must be tagged in GitHub with release notes and a reproducible build artifact (Docker image or static bundle). 
  \item \textbf{Fit Criterion:} Acceptance when: (a) core flows run on supported browsers; (b) documented REST endpoints respond to auth and telemetry; (c) dev deployment runs end-to-end using provided Docker-compose with README steps validated by at least one tester.
\end{itemize}

\section{Maintainability and Support Requirements}
\subsection{Maintenance Requirements}

\begin{itemize}
    \item \textbf{Code Maintainability}: The codebase must be modular, with clear separation of concerns to facilitate updates and debugging. Inline comments for non-obvious logic and updated README/module documentation are required, as specified in the development plan.
    \item \textbf{Version Control}: All changes must be tracked via GitHub, with descriptive commit messages and pull requests requiring at least one peer review to ensure maintainability.
    \item \textbf{Extensibility}: The system must support adding new features without requiring significant refactoring. This is achieved by using a modular architecture and Object oriented Design principles.
    \item \textbf{Documentation Updates}: Any change in behavior, interfaces, or setup instructions must be reflected in the documentation to ensure future developers can maintain the system. Local deployment instructions documented in the README to simplify setup for developers and maintainers.
\end{itemize}

\subsection{Supportability Requirements}

\begin{itemize}
    \item \textbf{Error Reporting}: The system must provide clear, user-friendly feedback for invalid moves. Logs or replays of game sessions must be available for debugging, as specified in the non-functional goals.
    \item \textbf{User Support}: A tutorial or visual guidance (stretch goal) must be provided to assist new players in understanding gameplay and dozenal scoring. This reduces the need for extensive manual support.
    \item \textbf{Cross-Platform Support}: The software must run on different web environments (Windows, macOS, or browsers). 
\end{itemize}

\subsection{Adaptability Requirements}

\begin{itemize}
    \item \textbf{Rule Flexibility}: The system must support toggling house rules (e.g., draw-until-playable, stacking eights) via a rule configurator (stretch goal), allowing adaptation to different play styles without code changes.
    \item \textbf{Scalability for Players}: The architecture must accommodate extending from two-player (MVP) to 3--4 player games (stretch goal) by modifying session management and turn logic.
    \item \textbf{Numeric System Extensibility}: The scoring system must allow switching between dozenal and decimal displays, ensuring adaptability for users unfamiliar with base-12.
\end{itemize}

\section{Security Requirements}
\subsection{Access Requirements}
\begin{itemize}
  \item Role model: \textbf{Guest}, \textbf{Registered Player}, and \textbf{Administrator/Team Maintainer}. Define permitted APIs for each role.
  \item Registered players may access persistent profile data and match history for their account only.
  \item Administrators may access system logs and anonymized telemetry; no arbitrary user personal data access without consent.
\end{itemize}

\subsection{Integrity Requirements}
\begin{itemize}
  \item Server-authoritative game state: all moves validated server-side for any online session to prevent client tampering.
  \item Persistent data (user profiles, match results) must be stored atomically; partial writes are unacceptable.
  \item Backups: periodic DB snapshots for recovery as defined in deployment docs.
\end{itemize}

\subsection{Privacy Requirements}
\begin{itemize}
  \item Collect minimal PII: username and optional display name; e-mail only if explicitly provided for account recovery.
  \item Users must be informed (privacy notice) before data collection; opt-out option for telemetry must be available.
\end{itemize}

\subsection{Audit Requirements}
\begin{itemize}
  \item Maintain tamper-evident logs for administrative actions and system errors for at least 30 days.
  \item For online sessions, optionally retain replay logs (seed and sequence) to permit investigation of disputes; stored replays must be anonymized when used outside the originating account.
\end{itemize}

\subsection{Immunity Requirements}
\begin{itemize}
  \item The product shall be resilient to basic web threats (e.g., injection, CSRF) by following standard secure-coding practices and OWASP guidance.
  \item External penetration testing is a stretch goal; at minimum, use linting and dependency-audit tools in CI.
\end{itemize}

\section{Cultural Requirements}
\subsection{Cultural Requirements}

\begin{itemize}
    \item \textbf{Numeric System Accessibility}: The software must present dozenal (base-12) in an intuitive, non-disruptive way. This includes clear UI elements for dozenal scores (using \reflectbox{2} and \reflectbox{3} for 10 and 11) and optional tutorials (stretch goal) to explain dozenal notation to users unfamiliar with it.
    \item \textbf{Inclusivity}: The system must avoid cultural biases in its design, ensuring that gameplay and terminology (suits, ranks) are universally recognizable across cultures familiar with standard playing cards. No culturally specific references or imagery should be used in the UI to maintain broad accessibility.
    \item \textbf{Educational Alignment}: The software must align with educational goals by demonstrating the practical benefits of dozenal in a game context, making it appealing to students and educators. This supports the cultural shift toward exploring alternative numeric systems, as advocated by stakeholders like dozenal enthusiasts.
\end{itemize}

\section{Compliance Requirements}

\subsection{Legal Requirements}
The game must comply with intellectual property laws and digital content distribution regulations.
All assets (images, fonts, and sounds) used in the game must be open-source, royalty-free, or properly licensed.

\subsection{Standards Compliance Requirements}
The software shall follow standard software development practices such as version control (Git), documentation standards (LaTeX-based SRS), and accessibility guidelines (WCAG 2.1 Level AA).
The codebase should be compliant with modern C++/Python style conventions (PEP8 or equivalent).

\section{Open Issues}

\subsection{Which Supported bases?}
  \begin{itemize}
    \item \textbf{Description:} Decide whether to support only Decimal and Dozenal, or to include multiple other bases (Base-8: Octal, Base-16: Hexadecimal, Base-6: Senary, Base-9: Nonary).
    \item \textbf{Stakeholders:} Educators; Students.
    \item \textbf{Action:} 1. Fix inconsistencies within SRS documented about which number bases to implement. Discussion required.
    \item \textbf{Status:} Open.
    \item \textbf{Target resolution:} Educational stakeholders will give guidance on curriculum fit and scope.
  \end{itemize}

\subsection{Deck creation for supported bases}
  \begin{itemize}
    \item \textbf{Description:} Create physical or print-ready decks for additional number systems. (Decimal and Dozenal decks exist:\\
    \url{https://www.thegamecrafter.com/games/k6t}.)
    \item \textbf{Stakeholder:} Dr. Paul Rapoport
    \item \textbf{Action:} Design and create decks for Octal and Hexadecimal; estimate cost and lead time.
    \item \textbf{Resolution:} Dr. Rapoport will inquire and report back to the team with feasibility info.
    \item \textbf{Status:} Pending response.
  \end{itemize}

\subsection{Counting mechanics vs. player enjoyment and game understandability}
  \begin{itemize}
    \item \textbf{Description:} How to add meaningful counting mechanics (teaching) while keeping game fun and understandable? Current ideas include:
    \begin{itemize}
      \item For non-winners, sum remaining cards at end of round to reduce point tally.
      \item Trigger an arithmetic task each time a wild card (10) is played.
      \item Other lightweight counting mini-games embedded in rounds.
    \end{itemize}
    \item \textbf{Stakeholders:} Dr. Paul Rapoport, UI/UX Designers, Educators, Students.
    \item \textbf{Action:} Continue ideation and small-scale playtests to evaluate engagement.
    \item \textbf{Status:} Ongoing.
  \end{itemize}

\subsection{Multiplayer mode implementation decision (ISS-04)}
\begin{itemize}
  \item \textbf{Description:} Decide whether online multiplayer (server-authoritative WebSocket rooms, reconnection, scaling) is in-scope for MVP or deferred to a post-MVP release. Identify minimal online feature set if approved.
  \item \textbf{Stakeholders:} Course Instructor; Dr. Paul Rapoport; Developers; QA.
  \item \textbf{Action:} Convene a design decision meeting; produce an options analysis (local hot-seat vs server-authoritative) with estimated engineering effort and acceptance criteria.
  \item \textbf{Status:} Open.
  \item \textbf{Target resolution:} Decision recorded in GitHub Issue and linked to an implementation milestone or deferral note.
\end{itemize}

\subsection{Educational feedback granularity and optional hints (ISS-05)}
\begin{itemize}
  \item \textbf{Description:} Determine the default level of educational feedback (none, minimal, optional per-game setting). Rapoport recommended hints be optional to avoid over-assistance.
  \item \textbf{Stakeholders:} Dr. Paul Rapoport; Educators; Students; UX Designers.
  \item \textbf{Action:} Draft an “Hints/pedagogy” matrix for modes (Off / Minimal / Full), map to UI options, and prepare a small A/B playtest.
  \item \textbf{Status:} Open.
  \item \textbf{Target resolution:} Hints implemented as opt-in per-player or per-session; documented in Settings and Instructor Notes.
\end{itemize}

\subsection{Multiple-round scoring to 100 and base-consistent thresholds (ISS-06)}
\begin{itemize}
  \item \textbf{Description:} Clarify multi-round scoring rules (target score e.g., 100) and whether thresholds are expressed and accumulated in the active base (decimal or dozenal).
  \item \textbf{Stakeholders:} Dr. Paul Rapoport; Course Instructor.
  \item \textbf{Action:} Specify scoring rules and sample round calculations in both decimal and dozenal; include acceptance tests.
  \item \textbf{Status:} Open.
  \item \textbf{Target resolution:} SRS updated with explicit scoring calculation examples and unit tests in repo.
\end{itemize}

\subsection{Card deck cardinality and representation discrepancy (ISS-07)}
\begin{itemize}
  \item \textbf{Description:} Resolve inconsistency: SRS currently states \"52 cards\" (decimal) and elsewhere implies a different card count for dozenal (e.g., 64). Decide canonical deck construction per base and document mapping of ranks (0..?).
  \item \textbf{Stakeholders:} Developers; Dr. Paul Rapoport; Game Designers.
  \item \textbf{Action:} Produce a deck specification per base (ranks, face-cards, zero inclusion) and update Data Dictionary and Business Data Model.
  \item \textbf{Status:} Open.
  \item \textbf{Target resolution:} Deck spec reviewed and accepted; design files / test vectors added to repo.
\end{itemize}

\subsection{Rank ordering and rank semantics (Ace/1/face cards) (ISS-08)}
\begin{itemize}
  \item \textbf{Description:} Formalize rank ordering (is Ace low or high?) and whether face-cards participate in arithmetic rules; clarify how face cards map to numeric values when arithmetic is required.
  \item \textbf{Stakeholders:} Game Designers; Dr. Paul Rapoport.
  \item \textbf{Action:} Document rank-to-value mapping for each base and add example scenarios demonstrating validity checks (UC5).
  \item \textbf{Status:} Open.
  \item \textbf{Target resolution:} Data Dictionary updated to include numeric mapping for face cards and Ace.
\end{itemize}

\subsection{Sum-target rule ambiguity (10 vs 11 / base-dependence) (ISS-09)}
\begin{itemize}
  \item \textbf{Description:} Rapoport suggests using sum-to-11 (in base) rather than sum-to-10 to avoid duplication and to make face cards usable. Determine canonical “sum-target” and implications for move validity and pacing.
  \item \textbf{Stakeholders:} Dr. Paul Rapoport; Game Designers; Educators.
  \item \textbf{Action:} Evaluate both options via short gameplay simulations; choose target (10 or 11) and document trade-offs and acceptance tests.
  \item \textbf{Status:} Open.
  \item \textbf{Target resolution:} Update FR-3 and UC5 to reflect chosen rule; add test cases.
\end{itemize}

\subsection{Optional zero-card and deck-extension (ISS-10)}
\begin{itemize}
  \item \textbf{Description:} Evaluate whether to include a zero card to support arithmetic rules involving face-card pairings (as suggested in review).
  \item \textbf{Stakeholders:} Dr. Paul Rapoport; Designers.
  \item \textbf{Action:} Prototype a deck variant and test for balance and educational clarity.
  \item \textbf{Status:} Open.
  \item \textbf{Target resolution:} Decision recorded; deck files added or rejected with rationale.
\end{itemize}

\subsection{Queen rule and optional house rules (ISS-11)}
\begin{itemize}
  \item \textbf{Description:} Include Queen-rule and other house-rule toggles (e.g., 2-rule) as optional settings in the Rule Configurator.
  \item \textbf{Stakeholders:} Players; Educators.
  \item \textbf{Action:} Add to Stretch Goals / Rule Configurator and document expected behaviour and UI toggle locations.
  \item \textbf{Status:} Open.
  \item \textbf{Target resolution:} Rule configurator UI/FRs added in a future sprint.
\end{itemize}

\subsection{Base-display and conversion policy (ISS-12)}
\begin{itemize}
  \item \textbf{Description:} Clarify whether UI will show both decimal and dozenal simultaneously or provide optional conversion toggles; Rapoport recommended making conversion optional.
  \item \textbf{Stakeholders:} UX Designers; Educators.
  \item \textbf{Action:} Add an options matrix in SRS: (A) Dozenal-only UI, (B) Dual-display (Dozenal+Decimal), (C) Optional conversion toggle. Select default.
  \item \textbf{Status:} Open.
  \item \textbf{Target resolution:} SRS updated and acceptance tests added verifying display modes.
\end{itemize}

\subsection{Mobile / phone responsiveness feasibility (ISS-13)}
\begin{itemize}
  \item \textbf{Description:} Rapoport doubts phone support is feasible; determine whether mobile support is stretch or omitted.
  \item \textbf{Stakeholders:} Developers; Dr. Paul Rapoport.
  \item \textbf{Action:} Classify “mobile” as stretch-goal or out-of-scope for MVP and document reasoning.
  \item \textbf{Status:} Open.
  \item \textbf{Target resolution:} Decision and update to \S10.responsiveness and Release Notes.
\end{itemize}

\subsection{Language support clarification (ISS-14)}
\begin{itemize}
  \item \textbf{Description:} Rapoport advised English-only for now; confirm language scope and mark translations as stretch.
  \item \textbf{Stakeholders:} Dr. Paul Rapoport; Course Instructor.
  \item \textbf{Action:} Set default language list (English) and mark other languages as stretch goals in SRS.
  \item \textbf{Status:} Open.
  \item \textbf{Target resolution:} SRS updated; internationalization backlog item created if required.
\end{itemize}

\subsection{Capacity target re-evaluation (ISS-15)}
\begin{itemize}
  \item \textbf{Description:} Reassess the 200 concurrent users testing target; confirm whether this is practical within the budget and hosting constraints.
  \item \textbf{Stakeholders:} Team Lead; DevOps; Dr. Paul Rapoport.
  \item \textbf{Action:} Produce an estimate of server costs and a scaled test plan; consider lower initial target (e.g., 20--50) for MVP.
  \item \textbf{Status:} Open.
  \item \textbf{Target resolution:} Update Capacity Requirements and CI load plan.
\end{itemize}

\subsection{Option A ambiguity (ISS-16)}
\begin{itemize}
  \item \textbf{Description:} Clarify “Option A: Local-first 2P hot-seat” — whether it implies two players on same device or AI opponent; Rapoport flagged confusion.
  \item \textbf{Stakeholders:} Team; Course Instructor.
  \item \textbf{Action:} Update Implementation Options with precise definitions and demo acceptance criteria for Option A and Option B.
  \item \textbf{Status:} Open.
  \item \textbf{Target resolution:} Implementation Options section clarified and accepted.
\end{itemize}

\subsection{Animations and hand ordering requirement (ISS-17)}
\begin{itemize}
  \item \textbf{Description:} Define card ordering animation spec (how cards are sorted and animated) and ensure it is included in Look-and-Feel Requirements.
  \item \textbf{Stakeholders:} UI/UX; Frontend Developers.
  \item \textbf{Action:} Draft a brief spec and add to \S10 Style Requirements; include accessibility considerations for motion.
  \item \textbf{Status:} Open.
  \item \textbf{Target resolution:} Animation spec committed and demoed in PoC.
\end{itemize}

\subsection{Reuse of existing domain and cost feasibility (ISS-18)}
\begin{itemize}
  \item \textbf{Description:} Investigate possibility of reusing existing dozenal-domain names or prior projects (Rapoport note) to reduce brand/setup costs.
  \item \textbf{Stakeholders:} Team Liaison; Dr. Paul Rapoport.
  \item \textbf{Action:} Research available domains and prior dozenal projects; report cost/availability and licensing constraints.
  \item \textbf{Status:} Open.
  \item \textbf{Target resolution:} Domain decision and purchase plan or deferral documented.
\end{itemize}

\subsection{Missing Fit Criteria and placeholder content (ISS-19)}
\begin{itemize}
  \item \textbf{Description:} Several sections still contain \verb|\lips| placeholders and lack explicit Fit Criteria (measurable acceptance criteria).
  \item \textbf{Stakeholders:} All authors; Document Owner.
  \item \textbf{Action:} Replace placeholders with substantive requirements and add Fit Criteria for each section before submission; track in issue tracker.
  \item \textbf{Status:} Open.
  \item \textbf{Target resolution:} All placeholders replaced and Fit Criteria added; document review pass.
\end{itemize}
  
\subsection{Fit criterion:}
  \begin{itemize}
    \item Each open item has a GitHub Issue.
    \item Each Issue lists owner, stakeholders explicit next-action, and a tentative resolution date or review milestone.
    \item Closure requires documented decision, implementation plan, or formal deferral with rationale.
  \end{itemize}

\section{Off-the-Shelf Solutions}

\subsection{Ready-Made Products}
Existing Crazy 8s card games (e.g., UNO or digital clones) offer partial gameplay models, but none integrate an educational Dozenal arithmetic component.
No direct off-the-shelf solution currently fulfills both entertainment and mathematical learning objectives.

\subsection{Reusable Components}
\begin{itemize}
    \item Card rendering engines from open-source projects such as \textit{Pygame} or \textit{Godot} assets.
    \item Math libraries for number-base conversion (decimal $\leftrightarrow$ Dozenal).
    \item UI component libraries for game menus, card animations, and scoreboards.
\end{itemize}

\subsection{Products That Can Be Copied}
Some structural aspects (turn management, shuffling algorithms) can be adapted from existing open-source card game repositories, provided licensing terms (e.g., MIT, GPL) are respected.
However, educational Dozenal mechanics must be developed in-house to align with project-specific learning goals.


\section{New Problems}
\subsection{Effects on the Current Environment}
\begin{itemize}
	\item The system is a newly devleoped web-based game and does not replace or interfere with any existing enviroment, minimal impact is expected aside from standard hosting and network usage.
\end{itemize}
\subsection{Effects on the Installed Systems}
\begin{itemize}
	\item No existing software systems are modified or replaced by this product. The game operates independently on standard browsers and web servers.
\end{itemize}
\subsection{Potential User Problems}
\begin{itemize}
	\item Users may experience confusion if base-conversion rules are misunderstood. These issues will be mitigated through clear feedback, tutorials, and consistent UI design.
\end{itemize}
\subsection{Limitations in the Anticipated Implementation Environment That May
Inhibit the New Product}
\begin{itemize}
	\item The main limitation is dependency on stable internet connectivity. Poor network conditions may degrade real-time synchronization or cause delayed responses.
\end{itemize}
\subsection{Follow-Up Problems}
\begin{itemize}
	\item As the system evolves, maintaining compatibility with browser updates and third-party libraries (e.g., React, Socket.io) may introduce future maintenance challenges.
\end{itemize}
\section{Tasks}
\subsection{Project Planning}
\begin{itemize}
	\item The project life cycle will follow the deliverable outline for SFWRENG 4G06: Capstone. By April the project must be completed in its entirety.
\end{itemize}
\subsection{Planning of the Development Phases}
\begin{itemize}
	\item Requirements and Design Phase - Gather functional and non-functional requirements, identifying key components.
	\item Prototyping Phase - Develop an early functional prototype focusing on core interactions and user interface flow.
	\item MVP Phase - Implement the main gameplay logic, user authentication, and basic scoring system as our MVP.
	\item Finalize Phase - Polish the user interface, improve performance, deploy the final version to the hosting environment and prepare presentation.
	
\end{itemize}

\section{Migration to the New Product}
Not applicable.

% =========================
% 23. Costs
% =========================
\section{Costs}

\subsection{Assumptions}
\begin{itemize}
  \item Academic, non-commercial deployment targeting a small user group during the term.
  \item Free tiers are acceptable for hosting and CI where reliability is sufficient for demos.
  \item Budget ceiling: 500 CAD (see Section ``Budget Constraints'').
\end{itemize}

\subsection{One-time Costs}
\begin{table}[hp]
  \caption{One-time Purchases (CAD)}\label{tab:one_time_costs}
  \begin{tabularx}{\textwidth}{lXrrr}
    \toprule
    \textbf{Item} & \textbf{Purpose} & \textbf{Unit} & \textbf{Total} \\
    \midrule
    Domain name (1 year) & Simple memorable URL for demos & 1 & 20 \\
    \midrule
    \multicolumn{4}{r}{\textbf{Subtotal}} & \textbf{20} \\
    \bottomrule
  \end{tabularx}
\end{table}

\subsection{Recurring Costs}
\begin{itemize}
  \item App hosting utilize free tier where possible
  \item DB hosting and Free tier Postgres, small instance
  \item Domain name renweal cost could be recurring if we plan on hosting it longer term
\end{itemize}

\subsection{Total and Headroom}
\noindent Estimated total spend for the term: \textbf{100 CAD}. This stays within the 500 CAD cap and leaves headroom for risk mitigation or stretch features.

\subsection{Cost Control Plan}
\begin{itemize}
  \item Prefer free tiers for hosting, CI, and CDN. Upgrade only if load or reliability requires it.
  \item Reuse open-source UI kits and icon packs with permissive licenses.
  \item Cap incentives to pre-approved number of sessions.
\end{itemize}

\section{User Documentation and Training}


\subsection{User Documentation Requirements}
\begin{itemize}
  \item \textbf{In-app help}: Contextual tooltips for controls, hover help for Dozenal terms, and an always-available ``How to play'' panel.
  \item \textbf{Quick Start}: Setup, start a match, play a turn, view scores. Written for first-time users.
  \item \textbf{Rules and Dozenal guide}: Clear rules of Crazy Eights plus a simple Dozenal primer with examples for A and B, and conversions between base 10 and base 12.
  \item \textbf{FAQ}: Troubleshooting (cannot play a card, reconnect flow, what counts as a valid move).
\end{itemize}

\begin{itemize}
  \item \textbf{In-app help}: Contextual tooltips for controls, hover help for Dozenal terms, and an always-available ``How to play'' panel.
  \item \textbf{Quick Start}: Setup, start a match, play a turn, view scores. Written for first-time users.
  \item \textbf{Rules and Dozenal guide}: Clear rules of Crazy Eights plus a simple Dozenal primer with examples for A and B, and conversions between base 10 and base 12.
  \item \textbf{FAQ}: Troubleshooting (cannot play a card, reconnect flow, what counts as a valid move).
\end{itemize}

\subsection{Training Requirements}
\begin{itemize}
  \item \textbf{Onboarding tutorial}: 3 to 5 steps covering play a card, draw a card, wild eight, and reading Dozenal scores. Skippable and repeatable.
  \item \textbf{Practice mode}: Solo mode against a simple bot to learn pace and rules without pressure.
\end{itemize}


% ---------------------------
% Section 25: Waiting Room (Stretch / Unimplemented Requirements)
% This section contains only unimplemented / stretch requirements as requested.
% Requirements are formatted to mirror the corresponding SRS sections
% (Look & Feel -> Section 10, Usability -> Section 11, Performance -> Section 5 / 12, etc.)
% ---------------------------

\section{Waiting Room (Stretch Requirements)}

\subsection{Purpose and scope}
This section lists unimplemented features (stretch goals) relating to the Crazy 10s game project. Each item below is intentionally classified as a post-MVP requirement; these will be considered for Crazy10s v1.1 (Rank 1) or v1.2 (Rank 2) per the urgency ranking in the very bottom of this section.

\subsection{Functional Stretch Requirements}
\begin{enumerate}
  
  \item \textbf{4-player match support (Stretch-L2)}\\
  \textbf{Description:} Extend session logic to allow 3--4 players, clear turn rotation, and UI to display additional hands.\\
  \textbf{Form (FR-style):} Add FR: "Multi-player session management must support up to 4 players with deterministic turn order and correct scoring."\\
  \textbf{Motivation:} Increased replayability and social gameplay.\\
  \textbf{Considerations:} Complexity in balancing learning vs. play-time; may increase server load.\\
  \textbf{Fit Criterion:} A 4-player match can be started, played to completion, and score computed correctly.
  
  \item \textbf{Invite and classroom session tools (Stretch-L1)}\\
  \textbf{Description:} Teachers create class sessions, bulk-invite students, and view join status.\\
  \textbf{Form:} Teacher dashboard extension FR.\\
  \textbf{Motivation:} Simplify classroom management and improve adoption.\\
  \textbf{Fit Criterion:} Teacher creates a session and sees join statuses in real time in the lobby.
\end{enumerate}

\subsection{UI / Look-and-Feel Stretch Requirements (mapped to Section 10)}
\begin{enumerate}
  \item \textbf{In-game optional hints (Stretch-U1)}\\
  \textbf{Appearance / Style Form:} Hints shall be available as an opt-in toggle in the lobby settings (per-player or per-session). Visual hint styles: glowing border, subtle tooltip.\\
  \textbf{Motivation:} Supports novice players during early learning but avoid over-assistance for experienced users.\\
  \textbf{Considerations:} Hints must be accessible (ARIA) and optional; do not clutter the interface by default.\\
  \textbf{Fit Criterion:} A player toggles hints in the lobby and receives contextual, non-blocking hints during gameplay when enabled.
  
  \item \textbf{Detailed onboarding preview in lobby (Stretch-U1)}\\
  \textbf{Appearance Form:} Lobby displays a short interactive primer about dozenal or the active base; includes a "Quick Try" button to demo the counting mechanic.\\
  \textbf{Motivation:} Lowers barrier to entry for classroom audiences.\\
  \textbf{Fit Criterion:} Primer launches from lobby and completes without entering a full match.
\end{enumerate}

\subsection{Education / Learning Stretch Requirements (mapped to Section 11)}
\begin{enumerate}
  \item \textbf{Advanced arithmetic mini-challenges (Stretch-E1)}\\
  \textbf{Description / Form:} When enabled in lobby, certain wild-card plays trigger short arithmetic mini-challenges (e.g., compute sum in active base). These are optional and configurable.\\
  \textbf{Motivation:} Deepen learning for engaged classes.\\
  \textbf{Considerations:} Must be skippable and have accessibility support; avoid disrupting game flow.\\
  \textbf{Fit Criterion:} When enabled, mini-challenges appear at correct trigger points and accept valid answers in the active base.
\end{enumerate}

\subsection{Internationalization and Language Stretch Requirements (mapped to Section 11.2)}
\begin{enumerate}
  \item \textbf{Optional language support (Stretch-I2)}\\
  \textbf{Description:} Add support for one additional language (e.g., French) as a stretch feature.\\
  \textbf{Form:} UI strings externalized; language selectable in lobby settings.\\
  \textbf{Motivation:} Broaden potential evaluators/users beyond English.\\
  \textbf{Considerations:} Translation quality is critical for pedagogical text; may require SME review.\\
  \textbf{Fit Criterion:} UI renders in selected language and sample dozenal primer is translated without truncation.
\end{enumerate}

\subsection{Performance / Capacity Stretch Requirements (mapped to Section 12)}
\begin{enumerate}
  \item \textbf{Higher concurrent capacity (Stretch-P2)}\\
  \textbf{Description:} Scale hosting to support >200 concurrent users for studies or demonstrations.\\
  \textbf{Form:} Performance requirement with load-test acceptance criteria.\\
  \textbf{Motivation:} Useful for large demo sessions or class-wide studies.\\
  \textbf{Considerations:} Higher cost and CI load-testing required.\\
  \textbf{Fit Criterion:} Simulated load test demonstrates system remains responsive per p95 latency target at target concurrency.
\end{enumerate}

\subsection{Integration / Deck Production Stretch Requirements}
\begin{enumerate}
  \item \textbf{Physical deck production workflow (Stretch-D2)}\\
  \textbf{Description:} Provide printable/print-on-demand assets and ordering instructions to create physical dozenal, octal, or hex decks.\\
  \textbf{Form:} Documentation and asset package in repo.\\
  \textbf{Motivation:} Supports tactile classroom use and outreach.\\
  \textbf{Considerations:} Licensing and cost to be estimated.\\
  \item \textbf{Fit Criterion:} Provided print assets produce a proof print and match on-screen representations.
\end{enumerate}

% ---------------------------
% Urgency ranking and release buckets
% Rank 1 = high priority stretch items (v1.1). Rank 2 = lower priority (v1.2).
% ---------------------------

\subsection{Urgency Ranking}
Each unimplemented stretch requirement above is assigned an urgency rank:
\begin{itemize}
  \item \textbf{Rank 1 (v1.1)}: High-priority stretch items likely to be scheduled immediately after MVP if resources permit.
  \item \textbf{Rank 2 (v1.2)}: Lower-priority stretch items for later releases or exploratory work.
\end{itemize}

\subsection{Crazy10s v1.1 (Rank 1) --- Priority stretch items}
\begin{itemize}
  \item Invite \& classroom session tools (Stretch-L1)
  \item In-game optional hints (Stretch-U1)
  \item Advanced arithmetic mini-challenges (Stretch-E1)
  \item Physical deck production workflow (Stretch-D2) --- planning/asset creation phase
\end{itemize}

\subsection{Crazy10s v1.2 (Rank 2) --- Lower priority stretch items}
\begin{itemize}
  \item 4-player match support (Stretch-L2)
  \item Detailed onboarding preview in lobby (additional polish) (Stretch-U1)
  \item Optional language support (Stretch-I2)
  \item Higher concurrent capacity (Stretch-P2)
\end{itemize}

\section{Ideas for Solution}
\subsection{Architecture Overview}
\begin{itemize}
  \item \textbf{Frontend}: React with TypeScript. State managed via a small store (Zustand or Redux Toolkit). WebSocket client for live turns. Component library and keyboard-first interactions.
  \item \textbf{Backend}: Node.js with TypeScript. HTTP API for auth and lobby. WebSocket for game sessions and events. Server-authoritative game state.
  \item \textbf{Data}: Postgres for user profiles, match history, and telemetry. In-memory room state with periodic snapshots to DB.
  \item \textbf{Game engine}: Pure TypeScript module with deterministic rules, validators, scoring, and base conversion utilities. No UI concerns.
  \item \textbf{CI/CD}: GitHub Actions for lint, tests, type-checks, and deploy to a free-tier host.
\end{itemize}

\subsection{Implementation Options}
\begin{tabularx}{\textwidth}{lX}
  \toprule
  \textbf{Option} & \textbf{Summary, Pros, Cons} \\
  \midrule
  A. Local-first 2P hot-seat & \textit{Summary}: Single browser, two players, no backend. \textit{Pros}: Fast MVP, minimal infra. \textit{Cons}: No remote play, no persistence. \\
  \midrule
  B. Server-authoritative WebSocket & \textit{Summary}: Lobby, rooms, turns via WS. \textit{Pros}: Fair play, replay logs, reconnect support. \textit{Cons}: More code and testing. \\
  \midrule
\end{tabularx}

\subsection{Recommended Path}
\begin{enumerate}
  \item Build the game engine as a pure library with full tests.
  \item Ship Option A for fast validation and UI polish.
  \item Upgrade to Option B for sessions, persistence, and reconnection.
\end{enumerate}

\subsection{Key Non-functional Techniques}
\begin{itemize}
  \item \textbf{Fairness}: Server-side validation for all moves. Shuffle with seeded RNG and record seed for audits.
  \item \textbf{Resilience}: Rejoin token and state rehydrate on reconnect.
  \item \textbf{Accessibility}: Semantic HTML, focus order, ARIA labels, and keyboard shortcuts for all core actions.
\end{itemize}

\newpage{}
\section*{Appendix --- Reflection}

\input{../Reflection.tex}

\input{../SRS_Reflection.tex}

\end{document}