\documentclass[12pt, titlepage]{article}

\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{hyperref}
\usepackage{tabularx}
\usepackage{float}
\usepackage{ltablex}
\hypersetup{
    colorlinks,
    citecolor=blue,
    filecolor=black,
    linkcolor=red,
    urlcolor=blue
}
\usepackage[round]{natbib}

\input{../Comments}
\input{../Common}

\begin{document}

\title{System Verification and Validation Plan for \\\progname{}} 
\author{
\authname
}
\date{\today}
	
\maketitle

\pagenumbering{roman}

\section*{Revision History}

\begin{tabularx}{\textwidth}{p{3cm}p{2cm}X}
\toprule {\bf Date} & {\bf Version} & {\bf Notes}\\
\midrule
Oct 24 & Alvin & System test functional requirements\\
Oct 26 & Ruida & Plan\\
Oct 27 & Jiaming & System test Non-functional requirements\\
Oct 27 & Ammar & Reviewed VnV Plan and created Issues \\
Oct 27 & Alvin & Fixed errors in FR tests\\
Oct 27 & Ruida & Fixed errors in Plan \\
Oct 27 & Alvin & VnV Plan Reflection \\
Oct 27 & Ammar & Acronyms and General Information \\
Nov 24 & Ruida & Fixed peer review issues and keep consistency\\
Mar 8 & Ruida & Change FR evaluation method into Manual UI\\
\bottomrule
\end{tabularx}


\newpage

\tableofcontents
\newpage
\pagenumbering{arabic}

\section{Symbols, Abbreviations, and Acronyms}

\renewcommand{\arraystretch}{1.2}
\begin{tabularx}{\textwidth}{l X}
\toprule
\textbf{Symbol / Acronym} & \textbf{Description} \\
\midrule
API & Application Programming Interface \\
CI & Continuous Integration \\
CD & Continuous Deployment \\
DB & Database \\
ERD & Entity Relationship Diagram \\
FR & Functional Requirement \\
NFR & Non-functional Requirement \\
SRS & Software Requirements Specification \\
V\&V & Verification and Validation \\
UI & User Interface \\
UX & User Experience \\
DBMS & Database Management System \\
Dozenal & Base-12 numerical system used in gameplay \\
Dec & Decimal numerical system (Base-10) \\
Dek & Dozenal digit equivalent to decimal 10 \\
El & Dozenal digit equivalent to decimal 11 \\
HTTP & Hypertext Transfer Protocol \\
TLS & Transport Layer Security \\
JSON & JavaScript Object Notation \\
CRUD & Create, Read, Update, Delete operations \\
MVP & Minimum Viable Product \\
IDE & Integrated Development Environment \\
GUI & Graphical User Interface \\
AI & Artificial Intelligence (for potential educational hints) \\
MG & \href{../Design/SoftArchitecture/MG.pdf}{Module Guide} \\
MIS &  \href{../Design/SoftDetailedDes/MIS.pdf}{Module Interface Specification} \\
HA & \href{../HazardAnalysis/HazardAnalysis.pdf}{HazardAnalysis} \\
SR & Safety Requirement (from \href{../HazardAnalysis/HazardAnalysis.pdf}{HazardAnalysis}) \\
QA & Quality Assurance \\
LTI & Learning Tool Interoperability (future extension) \\
CI/CD & Combined Continuous Integration and Continuous Deployment workflow \\
\bottomrule
\end{tabularx}

\noindent
This table summarizes the major symbols, abbreviations, and acronyms used throughout this Verification and Validation Plan. The terms originate from both the \href{../SRS/SRS.pdf}{SRS} and internal documentation, reflecting the technical, architectural, and educational contexts of the Crazy Tens project.

\newpage

%=============================
% Section 2: General Information
%=============================
\section{General Information}
This section provides an overview of the Crazy Tens project, outlining the software's purpose, key functionalities, and educational goals. It also defines the objectives of the verification and validation process, prioritizes quality attributes, assesses the challenge level and potential extras, and references supporting documentation to ensure alignment with project requirements.

%-----------------------------
\subsection{Summary}
The software being verified and validated is called \textbf{The Crazy Tens – A Counting Game}. It is an educational web-based card game designed to help users learn and practice arithmetic operations in different number bases, primarily Dozenal (Base 12) and Decimal (Base 10). The game provides interactive gameplay, Dozenal arithmetic challenges, score tracking, and base-conversion explanations to promote understanding of number systems.  

Key functionalities (adapted from the \href{../SRS/SRS.pdf}{SRS} Section 9) include:
\begin{itemize}
    \item Initiating and joining game sessions with other users in real time.
    \item Enforcing turn-based gameplay and validating moves under Dozenal rules.
    \item Calculating and displaying scores in both Decimal and Dozenal forms.
    \item Managing user profiles, accounts, and persistent game data.
    \item Providing Dozenal hints and explanations to reinforce learning objectives.
\end{itemize}
Educational support functions (FR 8–9) are considered out of scope for testing at this stage.

%-----------------------------
\subsection{Objectives}

The primary objective of this Verification and Validation Plan is to ensure that the Crazy Tens application satisfies all functional and non-functional requirements specified in the \href{../SRS/SRS.pdf}{SRS} and that the software is reliable, usable, and pedagogically effective.  
Specifically, the V\&V process aims to:
\begin{itemize}
    \item Verify the correctness, consistency, and completeness of the system design and implementation.  
    \item Validate that gameplay, scoring, and user experience meet the intended educational objectives.  
    \item Establish measurable quality standards for performance, usability, maintainability, and reliability.  
\end{itemize}

\subsubsection{Qualities to Prioritize}
The qualities listed below are prioritized in the verification and validation process to focus on attributes that enhance the educational impact, user engagement, and long-term viability of the Crazy Tens application, ensuring it meets high standards for reliability, performance, and maintainability.
\begin{table}[H]
\centering
\caption{Qualities to Prioritize}
\begin{tabularx}{\textwidth}{p{3cm}p{4.5cm}X}
\toprule
\textbf{Quality} & \textbf{Fit Criteria} & \textbf{Reasoning} \\
\midrule
Reliability & System uptime $\geq$ 99\%; no unhandled exceptions during gameplay & Reliability ensures stable multiplayer sessions and accurate scoring across sessions. \\
Scalability / Flexibility & Support up to 50 concurrent users; modular game engine for new base decks & Essential for future feature expansion such as new number bases and additional game modes. \\
Performance & Average UI latency $<$ 200\,ms; 95th percentile $<$ 350\,ms & A responsive interface ensures enjoyable gameplay and maintains learning engagement. \\
Usability & $\geq$ 80\% user task success rate in usability tests; average survey rating $\geq$ 4/5 & A user-friendly GUI encourages participation and reinforces educational motivation. \\
Understandability & New players learn rules within 4 minutes; tutorial completion $>$ 90\% & Ensures ease of learning and accessibility for first-time players. \\
Enjoyability & Post-play survey rating $\geq$ 4/5 on ``fun'' metric & Engagement sustains the educational value of the game. \\
Availability & Game accessible 24/7; server downtime $<$ 1 hour/month & Availability supports consistent access and data integrity. \\
Maintainability & $\geq$ 80\% code coverage; zero critical ESLint errors & Facilitates long-term sustainability and efficient issue resolution. \\
Testability & All modules link to test cases; full CI coverage $\geq$ 80\% & Enables systematic verification and smooth CI/CD workflows. \\
\bottomrule
\end{tabularx}
\end{table}

\subsubsection{Trivial Qualities}
This subsection outlines qualities that are essential but straightforward to achieve given the project's scope, requiring minimal additional effort beyond standard implementation practices to satisfy basic correctness and security needs.
\begin{table}[H]
\centering
\caption{Trivial Qualities}
\begin{tabularx}{\textwidth}{p{3cm}p{4.5cm}X}
\toprule
\textbf{Quality} & \textbf{Fit Criteria} & \textbf{Reasoning} \\
\midrule
Correctness & 100\% requirement-to-implementation traceability & Simple deterministic game logic ensures correctness with minimal complexity. \\
Security & TLS 1.2 enforced; password hashing verified via test suite & Login security is necessary but treated as routine for the educational MVP. \\
\bottomrule
\end{tabularx}
\end{table}

\subsubsection{Qualities to Deprioritize}
The following qualities are deprioritized as they fall outside the current project's primary objectives and constraints, allowing resources to be allocated toward core educational and functional goals instead.
\begin{table}[H]
\centering
\caption{Qualities Not Prioritized}
\begin{tabularx}{\textwidth}{p{3cm}p{4.5cm}X}
\toprule
\textbf{Quality} & \textbf{Fit Criteria} & \textbf{Reasoning} \\
\midrule
Interoperability & Single-platform (web) deployment; no mobile or cross-platform support & Out of scope for the current capstone; may be revisited in future iterations. \\
Reusability & Modular components documented but not abstracted for reuse & The project’s goal is educational demonstration, not software reuse. \\
\bottomrule
\end{tabularx}
\end{table}

%-----------------------------
\subsection{Challenge Level and Extras}

\subsubsection{Challenge Level}
In the beginning of the course, Professor Smith classified our challenge level as \textbf{basic}, as we were initially building a simple web-based card game. However, with additional features—multiple number-base decks, player authentication and matching, database persistence, and a reduced team of four—the project scope now fits an \textbf{intermediate} challenge level.

\subsubsection{Extras}
\paragraph{Norman’s Principles Report}
This extra is practical for our project because the graphical user interface and interaction design are central to player engagement and learning. Applying Norman’s principles helps refine visual cues and user feedback, both essential for usability and educational clarity.  
\begin{itemize}
    \item \textbf{Visibility} – Ensures players can easily identify playable cards and actions.  
    \item \textbf{Feedback} – Provides immediate visual and auditory responses to user moves.  
    \item \textbf{Affordance} – GUI elements (buttons, cards) clearly suggest their use.  
    \item \textbf{Mapping} – Card and control layouts intuitively match player expectations.  
    \item \textbf{Constraints} – Prevents illegal moves or inputs via interface restrictions.  
    \item \textbf{Consistency} – Uniform design promotes comfort and predictability across sessions.  
\end{itemize}
Evaluating the design through these principles promotes balanced usability and pedagogical effectiveness.

\paragraph{Usability Report}
For this extra, we will conduct structured usability testing following HCI best practices. The testing will include:
\begin{itemize}
    \item Clearly defined testing goals and quantifiable success criteria.  
    \item Predefined gameplay tasks (e.g., start match, make valid move, view results).  
    \item Post-session surveys assessing clarity, engagement, and satisfaction.  
\end{itemize}
This extra will help quantify user experience metrics and identify friction points prior to final rollout, ensuring the game is both intuitive and enjoyable for its educational audience.

%-----------------------------
\subsection{Relevant Documentation}
\begin{itemize}
    \item \textbf{SRS} – \href{https://github.com/The-Crazy-Four-Games/Crazy-Eights-Game/blob/main/docs/SRS-Volere/SRS.pdf}{Software Requirements Specification (SRS)}  
    \item \textbf{MG} – \href{https://github.com/The-Crazy-Four-Games/Crazy-Eights-Game/blob/main/docs/Design/SoftArchitecture/MG.pdf}{Module Guide (MG)}  
    \item \textbf{MIS} – \href{https://github.com/The-Crazy-Four-Games/Crazy-Eights-Game/blob/main/docs/Design/SoftDetailedDes/MIS.pdf}{Module Interface Specification (MIS)}  
\end{itemize}

Each of these documents contributes essential context for this plan:
\begin{itemize}
    \item The \textbf{SRS} defines all functional and non-functional requirements forming the foundation for test design.  
    \item The \textbf{MG} describes the software architecture and module interactions that are verified through design and integration testing.  
    \item The \textbf{MIS} specifies detailed module interfaces and data flows necessary for unit-level verification and static analysis.  
\end{itemize}
Together, they ensure complete traceability from requirements to design and testing.
%=============================


\section{Plan}
This section details the comprehensive, multi-phase plan for the verification and validation (V\&V) of the " The Crazy Tens" educational card game, an application designed to teach different number bases through a variant of the Crazy Tens card game. It establishes the V\&V-related responsibilities of the development team, the processes for verifying all key project artifacts (Software Requirements Specification, System Design, Implementation), the specific tools to be leveraged for automation, and the validation strategy to ensure the final product meets its core educational and functional objectives.   



\subsection{Verification and Validation Team}

\begin{table}[H]
\centering
\caption{Verification and Validation Team Roles and Responsibilities}
\label{tab:vvteam}
\begin{tabularx}{\textwidth}{lX}
\toprule
\textbf{Name} & \textbf{Responsibilities} \\
\midrule
Ruida Chen & Owns SRS checklist and requirement traceability; leads ambiguity inspections; opens and triages \href{../SRS/SRS.pdf}{SRS} issues on GitHub. \\
Ammar Sharbat & Conducts MG/MIS walkthroughs; checks FR/NFR coverage; verifies pre/post-conditions in design. \\
Alvin Qian & Develops unit and integration tests; maintains CI coverage metrics; triages static analysis warnings. \\
Jiaming Li & Organizes stakeholder playtests and usability sessions; aligns validation with personas and client expectations. \\
\bottomrule
\end{tabularx}
\end{table}

\subsection{SRS Verification}
\textbf{Objective:}  
To ensure the Software Requirements Specification (\href{../SRS/SRS.pdf}{SRS}) is complete, consistent, verifiable, and aligns with the project goals and constraints defined by the client and supervisor.

\noindent \textbf{Scope:}  
This verification applies to all functional and non-functional requirements described in the \href{../SRS/SRS.pdf}{SRS}. It covers requirement clarity, consistency, completeness, and testability.  

\noindent \textbf{Supervisor Involvement:}  
The SRS verification process will be conducted under the supervision of \textbf{Dr.\ Paul Rapoport}.  
Dr.\ Rapoport will act as the primary reviewer and domain expert, ensuring that the documented requirements correctly reflect the intended educational goals and gameplay design.  
He will provide written and verbal feedback during the SRS review meeting and confirm whether the requirements meet the course expectations.  
Any clarifications or corrections raised by Dr.\ Rapoport will be recorded in the SRS issue tracker and addressed.

\noindent \textbf{Verification Techniques:}
\begin{itemize}
    \item \textbf{Checklist-based inspection:} Each requirement will be reviewed using a formal checklist to ensure it is unambiguous, measurable, and testable.  
    \item \textbf{Cross-traceability review:} Every functional requirement (FR) will be linked to at least one design component and one planned test case.  
    \item \textbf{Peer review:} Team members who did not author the section will perform independent reviews to prevent bias.  
    \item \textbf{Supervisor review:} Dr.\ Rapoport will conduct a targeted review session to evaluate correctness, completeness, and educational intent.
\end{itemize}

\noindent\textbf{Supervisor Involvement:}  
The SRS verification process will be formally reviewed under the supervision of \textbf{Dr.\ Paul Rapoport}.  
The review will take the form of a scheduled meeting lasting approximately 30--45 minutes during the week following the internal peer review.  

\begin{itemize}
    \item \textbf{Meeting preparation:}  
    Before the meeting, the team will prepare and send Dr.\ Rapoport a concise review package containing:
    \begin{enumerate}
        \item The finalized \href{../SRS/SRS.pdf}{SRS} document (PDF);  
        \item A one-page summary of critical or ambiguous requirements;  
        \item The SRS verification checklist used in internal inspection;  
        \item The traceability matrix linking requirements to design/test artifacts.
    \end{enumerate}

    \item \textbf{Structured discussion topics:}  
    During the meeting, the team will:
    \begin{enumerate}
        \item Present how each major functional area (Game, Scoring, Educational Support, User Management) meets the educational and usability goals;
        \item Ask Dr.\ Rapoport to identify unclear, incomplete, or pedagogically inconsistent requirements;
        \item Confirm mutual understanding of success criteria and measurable outcomes (e.g., gameplay flow, scoring accuracy, base conversion learning intent).
    \end{enumerate}

    \item \textbf{Feedback capture and follow-up:}  
    Comments and action items from the meeting will be recorded in the GitHub Issue Tracker under the tag \texttt{SRS-Review}, each with an assigned owner and deadline.  
    The SRS Lead will ensure all feedback is incorporated into the updated \href{../SRS/SRS.pdf}{SRS} before sign-off.

    \item \textbf{Supervisor:}  
    After corrections, Dr.\ Rapoport will be provided with a change summary.
\end{itemize}
\noindent \textbf{Checklist}

\begin{table}[H]
\centering
\caption{SRS Verification Checklist}
\label{tab:srs-checklist}
\begin{tabular}{|l|l|p{0.4\textwidth}|l|l|}
\hline
\textbf{Checklist Item ID} & \textbf{Category} & \textbf{Verification Question} \\ \hline
SRS-C-01 & Completeness & Have all Open Issues been resolved and their resolutions integrated?  \\ \hline
SRS-C-02 & Completeness & Has all placeholder content been replaced with substantive text? \\ \hline
SRS-C-03 & Testability & Does every functional requirement have a unique identifier? \\ \hline
SRS-C-04 & Testability & Does every requirement now have a specific, measurable, and unambiguous Fit Criterion? \\ \hline
SRS-C-05 & Consistency & Are the game rules consistent? (e.g., Is FR-3 consistent with PUC-5?)  \\ \hline
SRS-C-06 & Consistency & Is the technology stack (React, Node.js, Postgres) consistent across Sec 3.1, 13.2, and 26.1? \\ \hline
SRS-C-07 & Correctness & Do all requirements trace back to a stated Project Goal or Stakeholder? \\ \hline
SRS-C-08 & Traceability & Is the scope unambiguous? \\ \hline
SRS-C-09 & Feasibility & Can all requirements be realistically implemented within the project constraints? \\ \hline
\end{tabular}
\end{table}


\subsection{Design Verification}
\noindent \textbf{Objective}: To verify that the system design is a correct, complete, and feasible implementation of the verified \href{../SRS/SRS.pdf}{SRS}

\noindent \textbf{Process:} Design Walkthroughs \& Peer Review
\begin{itemize}
	\item The team will create design artifacts such as UML diagrams, database Entity-Relationship-Diagram (ERD), etc.
	\item Schedule formal review meetings: These will occur weekly during the design phase or at key milestones, Each meeting will last 45–60 minutes and involve the full team, with at least one session including Dr. Rapoport
	\item In these meetings, the team will "walk through" the design, explaining how it fullfills specific requirements from the \href{../SRS/SRS.pdf}{SRS}.
	\item The team will use the checklist below to challenge the design and ensure full traceability from requirements to design.
	\item Feedback capture and follow-up: All comments and action items will be recorded in GitHub Issues under the tag "Design-Review," with assigned owners and deadlines (e.g., resolution within 48 hours for critical issues). The design lead will ensure incorporation into updated artifacts before the next meeting or milestone.
	\item All identified defects will be logged as GitHub Issues.
\end{itemize}

\noindent \textbf{Checklist}
\begin{table}[H]
\centering
\caption{Design Verification Checklist}
\label{tab:design-checklist}
\begin{tabular}{|l|l|p{0.4\textwidth}|l|l|}
\hline
\textbf{Checklist Item ID} & \textbf{Category} & \textbf{Verification Question}  \\ \hline
DS-C-01 & Traceability & Does every component in the architecture map to one or more Functional Requirements? \\ \hline
DS-C-02 & Completeness & Does the design for the "Game Manager" (Sec 9.1) component explicitly implement all rules)? \\ \hline
DS-C-03 & NFR-Performance & Does the architecture support the 50 concurrent user requirement? \\ \hline
DS-C-04 & NFR-Security & Does the design explicitly address all security requirements, including "server-authoritative game state" ?  \\ \hline
DS-C-05 & NFR-Maintain. & Does the design adhere to the mandated stack (React, Node.js)?[1] Is it modular and extensible ?  \\ \hline
DS-C-06 & NFR-Usability & Does the UI/UX design explicitly address Accessibility and Learning?  \\ \hline
DS-C-07 & Interface & Are all API endpoints clearly defined?  \\ \hline
DS-C-08 & Data & Does the database schema (ERD) correctly model the Business Data Model (Sec 7.1) and Data Dictionary (Sec 7.2)? \\ \hline
\end{tabular}
\end{table}

\subsection{Verification and Validation Plan Verification}

\noindent \textbf{Objective}: To verify this VnVPlan for completeness, feasibility, internal consistency, and adherence to all course rubrics.

\noindent \textbf{Process:} Formal Peer Review
\begin{itemize}
	\item The entire teamshall conduct one full read-through of this document before submitting it.
	\item The team will use the checklist below, which is directly derived from the course grading rubric, to ensure all requirements have been met.
	\item After the team review, the plan shall be informally presented to the course supervisor to get a "feasibility check" before implementation begins, mitigating project risk.
\end{itemize}

\noindent \textbf{Checklist}
\begin{table}[H]
\centering
\caption{V\&V Plan Verification Checklist}
\label{tab:vvp-checklist}
\begin{tabular}{|l|p{0.5\textwidth}|l|l|}
\hline
\textbf{Checklist Item ID} & \textbf{Verification Question} \\ \hline
VVP-C-01 & Are team roles for V\&V clear, specific, and feasible? \\ \hline
VVP-C-02 & Is the SRS verification plan clear, specific, and feasible? \\ \hline
VVP-C-03 & Is the Design verification plan clear, specific, and feasible? \\ \hline
VVP-C-04 & Is the Implementation verification plan clear, specific, and feasible? \\ \hline
VVP-C-05 & Are the automated testing and verification tools specific?  \\ \hline
VVP-C-06 & Is the software validation plan clear, specific, and feasible?  \\ \hline
VVP-C-08 & Is the plan feasible given the team size and academic term timeline?  \\ \hline
\end{tabular}
\end{table}

\subsection{Implementation Verification}

\noindent \textbf{Objective}: To verify that the source code artifacts correctly implement the verified design, adhere to all coding standards, are free of common defects, and meet all non-functional requirements.

\noindent \textbf{Unit testing}
\begin{itemize}
	\item \textbf{Frontend}:All UI components, verifying correct rendering and user-interaction behavior.
	\item \textbf{Backend}: All API endpoints, authentication logic, and data models.
	\item \textbf{Game Logic}: This is the most critical module to unit test. Tests will cover every game rule, include happy path + all edge cases.

\end{itemize}
\noindent \textbf{Integration testing}
\begin{itemize}
	\item \textbf{Frontend}:API + DB (login/session/history), engine + UI interaction (play card → rule check → UI update).
\end{itemize}

\noindent \textbf{Static Verification:}  
    In addition to dynamic testing, static verification activities will include:
    \begin{itemize}
        \item \textbf{Code walk-throughs:} Weekly peer reviews where presents newly developed code to the team, explaining logic and verifying alignment with design contracts.  
        \item \textbf{Code inspection:} Checklist-based inspections for coding-standard compliance (naming, commenting, error handling).  
        \item \textbf{Static analyzers:}  
        Use of TypeScript’s --strict mode, ESLint rules, and CodeQL analysis for detecting unused variables, type mismatches, and security issues.  
        \item \textbf{Continuous Integration enforcement:}  
        The CI pipeline will fail automatically if linting, type checking, or static analysis errors occur.
    \end{itemize}


\subsection{Automated Testing and Verification Tools}

\noindent\textbf{Objective:}  
To ensure that software verification activities are repeatable, efficient, and integrated with the development workflow.

\noindent\textbf{Tools and Automation:}
\begin{itemize}
    \item \textbf{Jest} --- used for unit and integration testing of both frontend and backend components.
    \item \textbf{Playwright} --- performs automated end-to-end testing of the user interface.
    \item \textbf{ESLint \& Prettier} --- automatically enforce coding style and detect syntax or logical issues.
    \item \textbf{GitHub Actions CI/CD} --- runs all tests automatically on each push or pull request; generates coverage and linting reports.
    \item \textbf{Codecov} --- collects and visualizes code coverage results from CI.
\end{itemize}

\noindent\textbf{Automation Outcome:}  
Automated testing ensures that every commit is verified for correctness, code quality, and integration stability before merging into the main branch.

\subsection{Software Validation}

\noindent\textbf{Objective:}  
To confirm that the final system meets user needs, project goals, and the expectations of the client and supervisor.

\noindent\textbf{Scope:}  
Validation focuses on ensuring that the software behaves as intended by users and stakeholders, not only that it was built correctly.

\noindent\textbf{Validation Methods:}
\begin{itemize}
    \item \textbf{Stakeholder Review:}  
    Conduct a demonstration of the working prototype for Dr.\ Paul Rapoport.  
    Feedback will be collected and documented for any changes before final submission.
    
    \item \textbf{Task-based User Testing:}  
    Team members and sample users will perform core gameplay tasks (e.g., joining a lobby, playing a round, viewing results).  
    Observations will be recorded to identify usability or clarity issues.

    \item \textbf{Survey and Feedback:}  
    A short questionnaire will be used to gather feedback on ease of use, performance, and enjoyment.
\end{itemize}

\noindent\textbf{Success Criteria:}
\begin{itemize}
    \item All core gameplay and scoring functions work as described in the \href{../SRS/SRS.pdf}{SRS}.  
    \item Supervisor and users confirm that the software meets educational and functional goals.  
    \item No critical usability or stability issues remain unresolved.
\end{itemize}

\noindent\textbf{Deliverables:}  
Validation summary report including stakeholder feedback, test logs, and any final fixes implemented before release.


\section{System Tests}

This section defines end to end system tests that validate the software against the \href{../SRS/SRS.pdf}{SRS} Functional Requirements (FR-1..FR-17) for the MVP implementation state. Tests are grouped by related functionality to improve traceability and reuse of fixtures. Unless stated otherwise, tests assume a deterministic deck seed, two authenticated test users, and a clean database. All expected results are observable via the UI and server state exposed to the test harness.

\subsection{Tests for Functional Requirements}

The subsections below cover: (1) game flow, rule validation, special cards, and end conditions (\href{../SRS/SRS.pdf}{SRS} Game Manager: FR-1..FR-5), (2) scoring and valid move highlighting (\href{../SRS/SRS.pdf}{SRS} Score Manager and Highlight: FR-6..FR-9), (3) account access flows (Login Manager: FR-10..FR-13), and (4) persistence operations (Data Manager: FR-14..FR-17). Where tests rely on input constraints, they use the card value and move legality definitions in the \href{../SRS/SRS.pdf}{SRS}.

\textit{Note: While originally planned as automated Node console scripts, these Functional Requirements evaluated via Manual UI-based Testing on the deployed application to better validate the end-to-end integration of the frontend, backend, and real-time WebSocket engine under realistic network conditions. The exactly numeric values below (such as card values, suit) may be different in actual testing case}

\subsubsection{Game Manager: Start, Turn, Rules, Specials, End (FR-1..FR-5)}

This area verifies new game initialization, turn sequencing, rule validation for same suit or same value or sum equals 12 (base-12), handling of wild tens, and detecting the end of a game. It directly traces to FR-1 Start new game, FR-2 Turn management, FR-3 Rule validation, FR-4 Special cards, FR-5 End of game.

\paragraph{Start new game initializes state (ST-GM-01)}
\begin{enumerate}
\item{ST-GM-01\\}
\textbf{Control:} Manual UI

\textbf{Initial State:} No active sessions. Two users are authenticated and in the lobby. Deterministic deck seed S is configured.

\textbf{Input:} User A clicks New Game and invites User B. User B accepts.

\textbf{Output:} A new session is created with a shuffled deck, a discard starter card is placed, each player receives the configured hand size H, and the UI shows turn = User A.

\textbf{Test Case Derivation:} From FR-1 and \href{../SRS/SRS.pdf}{SRS} deck initialization semantics. With a fixed seed S, the initial state is uniquely determined.

\textbf{How test will be performed:} Using two browser windows or two physical devices, User A logs in, creates a room, and invites User B (or B joins via code). Confirm that the UI transitions to the Game Screen, both avatars show 7 cards in hand, the discard pile shows 1 top card, and the UI visually indicates it is User A's turn.
\end{enumerate}

\paragraph{Legal move: same suit (ST-GM-02)}
\begin{enumerate}
\item{ST-GM-02\\}
\textbf{Control:} Manual UI

\textbf{Initial State:} Active session. Discard top = 5$\heartsuit$. User A hand contains K$\heartsuit$ and others. Turn = User A.

\textbf{Input:} User A plays K$\heartsuit$.

\textbf{Output:} Move is accepted. Discard top becomes K$\heartsuit$. Turn advances to User B.

\textbf{Test Case Derivation:} FR-3 allows a move when suits match.

\textbf{How test will be performed:} Observe the discard pile top card suit. When it is User A's turn, select a card of the same suit from the hand and click the Play button. Confirm the card moves to the discard pile and the turn indicator shifts to User B.
\end{enumerate}

\paragraph{Legal move: sum equals 12 (base-12) (ST-GM-03)}
\begin{enumerate}
\item{ST-GM-03\\}
\textbf{Control:} Manual UI

\textbf{Initial State:} Discard top = 5$\diamondsuit$ (value 5). User A hand contains 7$\spadesuit$ (value 7). Turn = User A.

\textbf{Input:} User A plays 7$\spadesuit$.

\textbf{Output:} Move is accepted. Discard top becomes 7$\spadesuit$. Turn advances to User B.

\textbf{Test Case Derivation:} In base-12, 5 + 7 = 10$_{12}$ which equals 12 in decimal. FR-3 permits play when values sum to 12 base-12.

\textbf{How test will be performed:} Observe the top card's decimal value (e.g., 5). When it is User A's turn, select a card whose decimal value adds up to 12 with the top card (e.g., 7). Click Play and confirm the move is accepted and the turn advances.
\end{enumerate}

\paragraph{Special card: wild ten suit selection (ST-GM-04)}
\begin{enumerate}
\item{ST-GM-04\\}
\textbf{Control:} Manual UI

\textbf{Initial State:} Discard top = K$\clubsuit$. User A hand contains 8$\heartsuit$. Turn = User A.

\textbf{Input:} User A plays 8$\heartsuit$ and selects Spades as the new suit.

\textbf{Output:} Move is accepted. Discard shows 8 with chosen suit indicator = Spades. Only Spades or otherwise legal responses are allowed for the next player.

\textbf{Test Case Derivation:} FR-4 specifies 8s are wild and allow the player to declare a suit.

\textbf{How test will be performed:} When it is User A's turn, select a wildcard (a 10). A UI modal should appear asking to select a new suit (e.g., Spades). Select the suit and confirm the UI updates to show specifically that the forced suit is Spades, and that User B is bound by it.
\end{enumerate}

\paragraph{Illegal move is rejected with guidance (ST-GM-05)}
\begin{enumerate}
\item{ST-GM-05\\}
\textbf{Control:} Manual UI

\textbf{Initial State:} Discard top = 9$\diamondsuit$. User A hand contains Q$\clubsuit$ and no other legal card.

\textbf{Input:} User A attempts to play Q$\clubsuit$.

\textbf{Output:} Move is rejected. UI shows a polite message explaining why the move is invalid and highlights available actions: draw or play a legal card if any.

\textbf{Test Case Derivation:} FR-3 rejects moves that are not same suit, not same value, and do not sum to 12 base-12.

\textbf{How test will be performed:} During gameplay, observe that illegal cards in the UI hand are not highlighted. Attempt to click an illegal card. Confirm the UI does not allow the card to be selected or played, preventing the illegal move entirely.
\end{enumerate}

\paragraph{End of game detection (ST-GM-06)}
\begin{enumerate}
\item{ST-GM-06\\}
\textbf{Control:} Manual UI

\textbf{Initial State:} User A has 1 card, which is legal to play. User B has multiple cards.

\textbf{Input:} User A plays the last card.

\textbf{Output:} Game ends. Winner = User A. System transitions to score calculation and displays results.

\textbf{Test Case Derivation:} FR-5 requires ending the game when a player has no cards left.

\textbf{How test will be performed:} Play a normal round until User A plays their final card. Confirm the UI immediately transitions to a Round Over / Game Over summary screen declaring User A the winner and displaying total scores.
\end{enumerate}

\subsubsection{Score Features: Dual-base, Highlights (FR-6..FR-9)}

This area validates round scoring in decimal and Dozenal, correct conversion and display, and visual highlighting of valid moves. Education Support and hints are out of scope.

\paragraph{Score calculated and shown in decimal and Dozenal (ST-SC-01)}
\begin{enumerate}
\item{ST-SC-01\\}
\textbf{Control:} Manual UI

\textbf{Initial State:} Game just ended. Opponent remaining cards have numeric values 2, 4, 6 (per \href{../SRS/SRS.pdf}{SRS} value function).

\textbf{Input:} Trigger score calculation screen.

\textbf{Output:} Decimal total = 12. Dozenal total = 10$_{12}$. Both are displayed side by side.

\textbf{Test Case Derivation:} 2 + 4 + 6 = 12 decimal which equals 10 in base-12.

\textbf{How test will be performed:} Complete a round where the loser holds specific cards. Observe the Round Result popup. Verify that the "Points Gained" correctly summarizes the lost hand in both Decimal (e.g., 12) and Dozenal (e.g., 10$_{12}$) notations side by side.
\end{enumerate}

\paragraph{Valid moves highlighted exactly (ST-SC-03)}
\begin{enumerate}
\item{ST-SC-03\\}
\textbf{Control:} Manual UI

\textbf{Initial State:} Discard top = 4$\spadesuit$. Hand contains 4$\clubsuit$, 8$\diamondsuit$, 7$\heartsuit$, Q$\spadesuit$, 6$\clubsuit$.

\textbf{Input:} None beyond rendering the hand.

\textbf{Output:} Highlighted cards are exactly \{4$\clubsuit$, Q$\spadesuit$, 8$\diamondsuit$\}. 7$\heartsuit$ and 6$\clubsuit$ are not highlighted.

\textbf{Test Case Derivation:} Same value (4), same suit (Spades), and wild eight are valid. Others are invalid because 7 + 4 = 11 decimal which is not 10$_{12}$ and 6 + 4 = 10 decimal which is not 10$_{12}$.

\textbf{How test will be performed:} During User A's turn, visually inspect the on-screen hand. Verify that exactly the cards that match suit, value, sum to 12, or are wildcards are visually highlighted or raised, while all others are dimmed or disabled.
\end{enumerate}


\subsubsection{Login Manager: Account, Sessions, Guest, Validation (FR-10..FR-13)}

This area verifies account creation, login and logout, guest sessions, and credential checks.

\paragraph{Account creation creates unique user and session (ST-LM-01)}
\begin{enumerate}
\item{ST-LM-01\\}
\textbf{Control:} Manual UI

\textbf{Initial State:} No account exists for username \texttt{U}. Clean auth store.

\textbf{Input:} Submit sign up with \texttt{username=U}, \texttt{password=P} that meets policy.

\textbf{Output:} Account is created with unique \texttt{userId}. Password is stored as a salted hash (not plaintext). A logged-in session for \texttt{U} is active.

\textbf{Test Case Derivation:} FR-10 requires creation with unique username and password.

\textbf{How test will be performed:} Navigate to the registration page. Submit a new unique username and a valid password. Confirm that the UI logs the user in and redirects to the Lobby or Main Menu. Then, open an incognito window and attempt to register with the exact same username. Confirm the UI rejects the second attempt with an appropriate "username taken" error message.
\end{enumerate}

\paragraph{Login and logout preserve progress (ST-LM-02)}
\begin{enumerate}
\item{ST-LM-02\\}
\textbf{Control:} Manual UI

\textbf{Initial State:} Account \texttt{U} exists with prior game history \texttt{H0}. No active session.

\textbf{Input:} \texttt{login(U,P)} then start a game, finish one hand, \texttt{logout()}, then \texttt{login(U,P)}.

\textbf{Output:} Session is established on both logins. After re-login, history includes prior \texttt{H0} plus the new hand \texttt{H1}. No progress is lost at logout.

\textbf{Test Case Derivation:} FR-11 requires login and logout at any time without losing progress.

\textbf{How test will be performed:} Log in as User U. Play one complete game. Navigate to the profile page and note the match history. Click Logout. Navigate back to the login page and authenticate again as User U. Confirm that the profile page still shows the exact same match history.
\end{enumerate}

\paragraph{Guest mode creates temporary session (ST-LM-03)}
\begin{enumerate}
\item{ST-LM-03\\}
\textbf{Control:} Manual UI

\textbf{Initial State:} No active session.

\textbf{Input:} \texttt{createGuestSession()} then play a short hand.

\textbf{Output:} Session has \texttt{guest:true}. No persistent user record is created. On process restart or \texttt{endGuestSession()}, the profile is not retrievable.

\textbf{Test Case Derivation:} FR-12 allows a temporary session without login.

\textbf{How test will be performed:} On the landing page, click "Play as Guest". Confirm a temporary account (e.g., "Guest\_XXXX") is created and logs in immediately without password. Complete a game. Click Logout. Attempt to log in to that specific Guest account—verification passes if this is impossible, proving the profile was temporary and deleted.
\end{enumerate}

\paragraph{Credential validation gates access (ST-LM-04)}
\begin{enumerate}
\item{ST-LM-04\\}
\textbf{Control:} Manual UI

\textbf{Initial State:} Account \texttt{U} exists with password \texttt{P}. No active session.

\textbf{Input:} Attempt \texttt{login(U,'wrong')}, then \texttt{login(U,P)}.

\textbf{Output:} First attempt is rejected with an auth error. No session is created. Second attempt succeeds and creates a session.

\textbf{Test Case Derivation:} FR-13 requires validating credentials against stored records before granting access.

\textbf{How test will be performed:} Navigate to the login page. Enter a valid registered username but an intentionally incorrect password. Confirm the UI rejects the login with an "invalid credentials" message. Then, enter the correct password and confirm successful entry to the Lobby.
\end{enumerate}

\subsubsection{Data Manager: Storage, Retrieval, Update, Deletion (FR-14..FR-17)}

This area verifies secure storage of usernames, game history, and Dozenal scores, along with retrieval, update, and deletion.

\paragraph{User data is stored on events that require persistence (ST-DM-01)}
\begin{enumerate}
\item{ST-DM-01\\}
\textbf{Control:} Manual UI

\textbf{Initial State:} Authenticated user \texttt{U}. Clean data store.

\textbf{Input:} Finish a game where opponent holds cards with values \{2,4,6\}. Trigger save.

\textbf{Output:} A record exists for \texttt{U} containing username, a new game history entry with decimal total 12 and Dozenal 10$_{12}$.

\textbf{Test Case Derivation:} FR-14 requires secure storage of user data including game history and Dozenal scores.

\textbf{How test will be performed:} Log in and complete a game against an opponent. Navigate to the Profile page dynamically. Confirm that the recent game appears in the Match History list, showing correct Decimal and/or Dozenal scores matching the game's actual conclusion.
\end{enumerate}

\paragraph{Stored data can be retrieved on login or profile view (ST-DM-02)}
\begin{enumerate}
\item{ST-DM-02\\}
\textbf{Control:} Manual UI

\textbf{Initial State:} Data store contains prior records for \texttt{U}.

\textbf{Input:} \texttt{login(U,P)} then \texttt{getProfile(U)}.

\textbf{Output:} Retrieved profile includes username, cumulative game history, and Dozenal scores as saved.

\textbf{Test Case Derivation:} FR-15 requires retrieval of stored user data.

\textbf{How test will be performed:} Log in to an account that has previously played multiple games. Navigate to the Profile page. Confirm that the UI successfully fetches and renders the user's overall stats (win rate, total games) and the history of past matches accurately.
\end{enumerate}

\paragraph{Data updates after games and profile changes (ST-DM-03)}
\begin{enumerate}
\item{ST-DM-03\\}
\textbf{Control:} Manual UI

\textbf{Initial State:} Profile for \texttt{U} exists with history length \texttt{n}.

\textbf{Input:} Complete another game, change nickname, refresh and open profile page, check match history.

\textbf{Output:} History length becomes \texttt{n+1}. Profile \texttt{displayName} is updated. Timestamps reflect the latest update.

\textbf{Test Case Derivation:} FR-16 requires updating stored data after each game or profile change.

\textbf{How test will be performed:} Navigate to the Profile page and use the Settings/Edit Modal to change the user's Display Name to a new string. Save the changes. Refresh the entire web page (F5) and navigate back to Profile. Confirm the new display name persists correctly.
\end{enumerate}

\paragraph{User can permanently delete data (ST-DM-04)}
\begin{enumerate}
\item{ST-DM-04\\}
\textbf{Control:} Manual UI

\textbf{Initial State:} Profile and history exist for \texttt{U}.

\textbf{Input:} User enter the profile page, click the ``delete account'' button and confirm.

\textbf{Output:} User records, history, and scores are removed from the database. Login is rejected since the account data has been deleted or deactivated per policy.

\textbf{Test Case Derivation:} FR-17 requires permanent deletion upon request.

\textbf{How test will be performed:} Log in as User U. Navigate to the Profile page and click the "Delete Account" / "Danger Zone" button. Confirm the action logs the user out. Attempt to log back in with User U's credentials. Confirm the system rejects the login entirely, proving the profile was wiped.
\end{enumerate}


\subsection{Tests for Nonfunctional Requirements}

    \subsubsection{Performance and Responsiveness (NFR-1)}
    \textbf{Objective:} Verify that all user interactions, such as playing a card or updating the score, occur with a latency below 200\,ms under normal network conditions. \\

    \textbf{Type:} Dynamic, Manual UI \\

    \textbf{Initial State:} Running MVP build on localhost with two authenticated test users and a seeded deck. \\

    \textbf{Input / Condition:} Simulated play sessions of 100 rounds using Playwright scripts. \\

    \textbf{Expected Output / Metric:} Average response time $\leq 200$\,ms, 95th-percentile $\leq 350$\,ms; no dropped WebSocket messages. \\

    \textbf{How test will be performed:}
    Use Playwright performance APIs to measure latency between client events and UI updates. Aggregate results into a summary table through CI (GitHub Actions).
    If thresholds are exceeded, flag the run as a warning and create an issue.

    \subsubsection{Usability and User Satisfaction (NFR-2)}
    \textbf{Objective:} Assess how easily new users can understand and play the Dozenal Crazy Tens game. \\

    \textbf{Type:} Dynamic, Manual \\

    \textbf{Initial State:} Usable prototype deployed on a test server. Five participants who have never played the Dozenal version will take part in a guided session. \\

    \textbf{Input / Condition:} Each participant completes a 15-minute task sequence (start a game, play 3 rounds, view score explanation). \\

    \textbf{Expected Output / Metric:} At least 80\% of participants successfully finish the task without assistance; post-test survey average rating $\geq 4$ (out of 5) on clarity and enjoyment. \\

    \textbf{How test will be performed:}
    Observation and screen recording during gameplay, followed by a 5-question Likert survey (see Appendix 6.2).
    Feedback will be compiled into a usability report.

    \subsubsection{Stability and Robustness (NFR-3)}
    \textbf{Objective:} Confirm that the application handles unexpected network events and invalid inputs gracefully. \\

    \textbf{Type:} Dynamic, Manual UI + Manual Fault Injection \\

    \textbf{Initial State:} Running multi-client session connected via WebSocket. \\

    \textbf{Input / Condition:} Simulate network interruptions and send malformed game actions through a test harness. \\

    \textbf{Expected Output / Metric:} Application recovers without crash or data loss; users receive an error message ``Connection lost – reconnecting…'' and game state resyncs within 5 seconds. \\

    \textbf{How test will be performed:}
    Inject disconnects using Playwright’s network emulation tools. Review browser console and server logs for exceptions. Report mean recovery time and failure rate.

    \subsubsection{Maintainability and Code Quality (NFR-4)}
    \textbf{Objective:} Evaluate source-code consistency and test coverage as indicators of maintainability. \\

    \textbf{Type:} Static Analysis / Automated \\

    \textbf{Initial State:} Repository after successful build on GitHub Actions. \\

    \textbf{Input / Condition:} Run ESLint, Prettier, and CodeQL scans; collect coverage data via Codecov. \\

    \textbf{Expected Output / Metric:} No ESLint errors or critical CodeQL alerts; line coverage $\geq 80$\%. \\

    \textbf{How test will be performed:}
    Continuous Integration pipeline executes static analysis and unit testing jobs on each commit. Results are stored as badges in the repository README for transparency.



\subsection{Traceability Between Test Cases and Requirements}
This traceability matrix links each functional and non-functional requirement from the Software Requirements Specification (\href{../SRS/SRS.pdf}{SRS}) to the relevant system test cases, demonstrating comprehensive coverage and facilitating verification that all requirements are adequately tested.

\begin{table}[H]
    \centering
    \caption{Traceability Between Test Cases and Requirements}
    \label{TblTraceability}
    \begin{tabular}{|p{0.2\textwidth}|p{0.45\textwidth}|p{0.35\textwidth}|}
        \hline
        \textbf{Requirement ID} & \textbf{Description (from \href{../SRS/SRS.pdf}{SRS})} & \textbf{Associated Test Case(s)} \\ \hline

        FR-1 & Start a new game session with two players. & ST-GM-01 \\ \hline
        FR-2 & Manage player turns and enforce alternating actions. & ST-GM-02, ST-GM-04 \\ \hline
        FR-3 & Validate move legality (same suit, same value, or sum equals 12 in base-12). & ST-GM-02, ST-GM-03, ST-GM-05 \\ \hline
        FR-4 & Handle special cards (wild eight suit declaration). & ST-GM-04 \\ \hline
        FR-5 & Detect end-of-game condition and declare winner. & ST-GM-06 \\ \hline
        FR-6 & Compute total score in both decimal and dozenal formats. & ST-SC-01 \\ \hline
        FR-7 & Display score in dual-base format with toggling support. & ST-SC-04 \\ \hline
        FR-8 & Provide Dozenal arithmetic explanations and hints. & ST-SC-02 \\ \hline
        FR-9 & Highlight valid playable cards in the UI. & ST-SC-03 \\ \hline

        NFR-1 & Performance: all user interactions respond in under 200\,ms. & NFR-1 Performance and Responsiveness test \\ \hline
        NFR-2 & Usability: at least 80\% of users complete tasks successfully; survey rating $\geq$ 4/5. & NFR-2 Usability and User Satisfaction test \\ \hline
        NFR-3 & Stability: recovery from disconnects without data loss within 5\,s. & NFR-3 Stability and Robustness test \\ \hline
        NFR-4 & Maintainability: code quality verified via ESLint, CodeQL, and $\geq$80\% test coverage. & NFR-4 Maintainability and Code Quality test \\ \hline

    \end{tabular}
\end{table}

\section{Unit Test Description}

\wss{This section should not be filled in until after the MIS (detailed design
  document) has been completed.}

\wss{Reference your MIS (detailed design document) and explain your overall
philosophy for test case selection.}  

\wss{To save space and time, it may be an option to provide less detail in this section.  
For the unit tests you can potentially layout your testing strategy here.  That is, you 
can explain how tests will be selected for each module.  For instance, your test building 
approach could be test cases for each access program, including one test for normal behaviour 
and as many tests as needed for edge cases.  Rather than create the details of the input 
and output here, you could point to the unit testing code.  For this to work, you code 
needs to be well-documented, with meaningful names for all of the tests.}

\subsection{Unit Testing Scope}

\wss{What modules are outside of the scope.  If there are modules that are
  developed by someone else, then you would say here if you aren't planning on
  verifying them.  There may also be modules that are part of your software, but
  have a lower priority for verification than others.  If this is the case,
  explain your rationale for the ranking of module importance.}

\subsection{Tests for Functional Requirements}

\wss{Most of the verification will be through automated unit testing.  If
  appropriate specific modules can be verified by a non-testing based
  technique.  That can also be documented in this section.}

\subsubsection{Module 1}

\wss{Include a blurb here to explain why the subsections below cover the module.
  References to the MIS would be good.  You will want tests from a black box
  perspective and from a white box perspective.  Explain to the reader how the
  tests were selected.}

\begin{enumerate}

\item{test-id1\\}

Type: \wss{Functional, Dynamic, Manual, Manual UI, Static etc. Most will
  be automatic}
					
Initial State: 
					
Input: 
					
Output: \wss{The expected result for the given inputs}

Test Case Derivation: \wss{Justify the expected value given in the Output field}

How test will be performed: 
					
\item{test-id2\\}

Type: \wss{Functional, Dynamic, Manual, Manual UI, Static etc. Most will
  be automatic}
					
Initial State: 
					
Input: 
					
Output: \wss{The expected result for the given inputs}

Test Case Derivation: \wss{Justify the expected value given in the Output field}

How test will be performed: 

\item{...\\}
    
\end{enumerate}

\subsubsection{Module 2}

...

\subsection{Tests for Nonfunctional Requirements}

\wss{If there is a module that needs to be independently assessed for
  performance, those test cases can go here.  In some projects, planning for
  nonfunctional tests of units will not be that relevant.}

\wss{These tests may involve collecting performance data from previously
  mentioned functional tests.}

\subsubsection{Module ?}
		
\begin{enumerate}

\item{test-id1\\}

Type: \wss{Functional, Dynamic, Manual, Manual UI, Static etc. Most will
  be automatic}
					
Initial State: 
					
Input/Condition: 
					
Output/Result: 
					
How test will be performed: 
					
\item{test-id2\\}

Type: Functional, Dynamic, Manual, Static etc.
					
Initial State: 
					
Input: 
					
Output: 
					
How test will be performed: 

\end{enumerate}

\subsubsection{Module ?}

...

\subsection{Traceability Between Test Cases and Modules}

\wss{Provide evidence that all of the modules have been considered.}
				
%\bibliographystyle{plainnat}

%\bibliography{../../refs/References}

\newpage

\section{Appendix}

This is where you can place additional information.

\subsection{Symbolic Parameters}

The definition of the test cases will call for SYMBOLIC\_CONSTANTS.
Their values are defined in this section for easy maintenance.

\subsection{Usability Survey Questions?}

\newpage{}
\section*{Appendix --- Reflection}


The information in this section will be used to evaluate the team members on the
graduate attribute of Lifelong Learning.

\input{../Reflection.tex}

\begin{enumerate}
  \item What went well while writing this deliverable? 

During the writing of this deliverable, our team improved our understanding of how verification and validation activities fit into a software lifecycle.  We learned to trace requirements back to specific tests, and maintain consistency across project documents(\href{../SRS/SRS.pdf}{SRS} and Supervisor feedbacks). Overall, this deliverable helped us formalize our testing strategy and clarify the expectations for the Crazy Tens project.
  \item What pain points did you experience during this deliverable, and how
    did you resolve them?


Scope drift around base rules and wild card, cross-doc sync issues between \href{../SRS/SRS.pdf}{SRS} and VnV, and clarifying auth/data flows; we resolved these by parameterizing rules via config and FR ids, adding a small CSV trace matrix and change logs, and specifying salted hashing, session behavior, and delete flows mirrored by tests.
  \item What knowledge and skills will the team collectively need to acquire to
  successfully complete the verification and validation of your project?
  Examples of possible knowledge and skills include dynamic testing knowledge,
  static testing knowledge, specific tool usage, Valgrind etc.  You should look to
  identify at least one item for each team member.

Collectively we need stronger dynamic and static testing and specific tool skills; Alvin: CI and property-based testing coverage, Ruida: requirements-to-tests traceability and mutation testing, Ammar: authentication and data lifecycle verification, Jiaming: UI highlighting and scoring verification with basic accessibility.
  \item For each of the knowledge areas and skills identified in the previous
  question, what are at least two approaches to acquiring the knowledge or
  mastering the skill?  Of the identified approaches, which will each team
  member pursue, and why did they make this choice?

Alvin will set up GitHub Actions and add fast-check property tests for edge cases because it raises coverage with low overhead; Ruida will build a CSV trace matrix; Ammar will implement salted-hash, session, and CRUD delete tests because auth and data are MVP-critical; Jiaming will create a small Playwright suite and add axe checks in one target browser because it keeps scope focused while covering UI correctness and accessibility.
\end{enumerate}

\end{document}