\documentclass{article}


\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}

\usepackage{tabularx,booktabs,array,ragged2e,makecell}
\usepackage[none]{hyphenat}
\renewcommand\theadfont{\normalsize\bfseries}
\renewcommand{\arraystretch}{1.2}
\setlength{\tabcolsep}{6pt}
\usepackage{float}



\newcolumntype{L}{>{\RaggedRight\arraybackslash}X}

\title{Problem Statement and Goals\\\SE Software Engineering}
\author{
    Team \#25, The Crazy Four \\[1ex]
    Ruida Chen \\
    Ammar Sharbat \\
    Alvin Qian \\
    Jiaming Li \\
}
\date{22.09.2025}


\input{../Comments}
\input{../Common}


\begin{document}
    \maketitle

    \begin{table}[hp]
        \caption{Revision History} \label{TblRevisionHistory}
        \begin{tabularx}{\textwidth}{llX}
            \toprule
            \textbf{Date} & \textbf{Developer(s)} & \textbf{Change}\\
            \midrule
            9.20 & Jiaming Li & Goals and Stretch Goals\\
            9.22 & Jiaming Li & Separating FG and NFG\\
            9.22 & Jiaming Li & Reflection\\
            9.22 & Ammar Sharbat & Problem Statement\\
            \bottomrule
        \end{tabularx}
    \end{table}

    \section{Problem Statement}

    \subsection{Introduction - Decimal vs. Dozenal}
    The prevailing use of the Decimal number base (Base-10) is rooted in historical,
    cultural conventions as opposed to practical mathematical utility. Decimal relies on prime
    factors 2 and 5, which limit the number of fractions that terminate cleanly, 
    leading to many recurring decimals for simple ratios such as 1/3, 1/6, and even 1/12. 
    This leads to many practical problems in counting, scaling, measurement, and most importantly,
    computing, where repeating decimals are often problematic, leading to excessive inaccuracies
    in calculation, rounding errors, and disasters like the Pentium floating-point division bug in 1994,
    and the Ariane 5 rocket crash in 1996. The fact that the number 10 is so indivisible is a big
    contributor to these incidents. \\\\
    Furthermore, considering how commonly we count in Dozens as opposed to Decimals, some examples being:
    \begin{itemize}
    \item Days are counted in 12 hours
    \item Years are counted in 12 moons / 12 months
    \item Eggs, medicine and many other items are sold in dozens
    \item Feet are measured in 12 inches
    \item There are 12 ounces to a pound of weight
    \end{itemize}\\
    we see that Dozenal (Base-12), or Duodecimal counting is very common. Historically, many societies preferred counting by Dozens
    over counting by Decimals, and while there have been many reasons for this, the most practical one is that has four divisors
    outside itself and 1, (2, 3, 4, and 6) and all of these divisors are useful in a variety of scientific domains. 
    This allows for more efficient and intuitive representation of fractions,
    and moreso, this makes it much more versatile and practical for counting, measuring, and even
    computational tasks when comparing to Decimal.\\\\
    All of this considered, neither Dozenal nor any other number system will replace Decimal, because the mathematical
    tradition is deeply ingrained in Decimal counting, despite its inferiority. Moreover, even bringing up the
    topic of learning new number systems like Dozenal makes the most respected scientists roll their eyes,
    because they cannot practically use anything other than base-10, which rules all of Science.
    Nevertheless, hope lies with the next generation of thinkers, creators and builders to consider the
    possibilities of using a more practical counting, scaling and computational number system. From this, the
    opportunity and question is qualified: How do we encourage the next generation to consider using other number
    systems like Dozenal in their everyday lives?

    \subsection{The Problem}
    The problem our team (and supervisor Dr. Paul Rapoport) are tackling is introducing Dozenal (Base-12) into the educational system 
    and the lives of everyday people in a meaningful way.\\
    Modern education is deeply embedded around Decimal concepts, so teaching Base-12 requires not only new materials but also engaging ways
    to entice people to learn and try this numerical system.\\
    A practical way to do this is through a game, and ideally one that is easy to understand, 
    and is enjoyable for players so that barriers to learning can be prevented. 
    Research shows that game-based learning has become a prominent tool in education and the modern workforce.\\\\
    The problem this project will tackle is building a fun game that improves numeracy skills in Dozenal (and other number bases) for all players.
    The game suggested to us by Dr. Rapoport was Crazy Eights, but with a Twist.
    And so, we have to contstruct a new version of Crazy Eights that incorporates Dozenal arithmetic and scoring.\\
    We also need to build this game in a way that it can be accessed to people around the world. 
    For this, and so web-based deploymentis the best option.\\
    
    \subsection{Inputs and Outputs}
    
    \subsubsection{High-Level Inputs}
    The system accepts the following categories of input:
    \begin{itemize}
        \item \textbf{Player Actions:} Discrete user actions submitted during gameplay -- match actions (join, leave, restart), card selection, suit changes, chat, etc.
        \item \textbf{Numerical Base:} Selection of the number base (Decimal, Dozenal, or other bases) that determines deck composition, face ranks, scoring parameters and gameplay.
        \item \textbf{User Identity:} Authentication credentials, session tokens, and profile information that authorize players to join matches.
        \item \textbf{Game Context:} Current game state (hands, deck, discard pile, scores, turn order) needed to validate moves and compute state transitions within the game.
    \end{itemize}

    \subsubsection{High-Level Outputs}
    The system produces the following outputs:
    \begin{itemize}
        \item \textbf{Synchronized Game State:} Real-time updates to gameplay for all players (e.g. game creation, rule validation, special effects).
        \item \textbf{Numerical Outputs:} Values converted and accurately displayed in the active number base.
        \item \textbf{User Feedback / Validation:} Response signals indicating move legality, game success/failure, in-game messages (notifications, chat) to facilitate player behavior in-game.
        \item \textbf{Rendered User Interface:} Visual components presenting the game board, player hands, discard pile, scoreboard, lobbies, etc.
        \item \textbf{Persistent User Data:} Stored profiles, match history, and statistics enabling continuity and progress tracking.
    \end{itemize}

    \subsection{Stakeholders}
    Several groups are directly affected by the shortcomings of the Decimal number base and 
    stand to benefit from exploring and incorporating Dozenal as an alternative. Several stakeholder 
    groups also may be positively impacted by the creation of a card game on web that 
    teaches counting and mathematics, even if they may not seek the Dozenal aspect of the game.\\
    \textbf{Mathematicians}, particularly Dozenal and numerical mathematicsenthusiasts like Dr. Paul Rapoport
    are invested in advancing the theoretical and practical aspects of base-12. As we covered in the introduction,
    Dozenal has fewer constraints and flaws that is found in Decimal, and by evidence is a more coherent and precise
    number base for mathematics.\\\\
    Additionally, \textbf{Scientists} 
    will benefit from the improved divisibility and improved precision that Dozenal has to offer.
    \textbf{Computer Scientists}, who already work with multiple number bases (like binary, octal, hexadecimal)
    and who are seeking maximum precision and efficiency in their work, could leverage Dozenal, after learning it.\\\\
    Similarly, \textbf{Students} like ourselves, grade school students, and \textbf{Educators}, like teachers and Professors in STEM fields 
    are also key stakeholders. This is because cleaner mathematics and calculation procedures (that come with adoption of Dozenal) 
    would enhance mathematical understanding of several concepts in Engineering, Science and many other disciplines.\\\\
    \textbf{Educational Institutions} are also important, as theyshape curricula and would determine whether alternative 
    modes of thinking are introduced (like alternative number bases). Our team and Professor are part of an institution; 
    McMaster University, and through them we have the opportunity to influence our peers and future students in adopting Dozenal in their thinking.\\\\
    Regarding our end product (a \textbf{game}), there are several key stakeholders as well.\\
    \textbf{Parents} and \textbf{Children} are important stakeholders, because they are a key user base
    for web, mobile and card games. This game should be designed with their needs and preferences in mind, and should be designed 
    to be simple and engaging along with it's educational focus.\\\\
    \textbf{Gamers} and \textbf{Game Developers} are also stakeholders. Gamers may find value in a novel aspect of this game (an educational twist on a classic card game).
    Developers may be interested in the design and implementation of a game that incorporates new educational elements, and also numerical design.\\
    Finally, the \textbf{General Public} are indirectly affected by our project. Tradespeople, technicians, office workers, and everyday
    users of measurement systems may find practical utility in a web-based game that teaches numerical skills that they can use in their daily lives.\\\\
    The importance/priority of each stakeholder group is as follows.\\\\
    \textbf{Primary Stakeholders:}
    \begin{itemize}
        \item Mathematicians (and Dozenal Enthusiasts)
        \item Computer Scientists
        \item Other Scientists
        \item Students
        \item Educators
    \end{itemize}
    \textbf{Secondary Stakeholders:}
    \begin{itemize}
        \item Parents and Children
        \item Educational Institutions
    \end{itemize}
    \textbf{Other Stakeholders:}
    \begin{itemize}
        \item Gamers
        \item Game Developers
        \item General Public (tradespeople, technicians, office workers)
    \end{itemize}

    \subsection{Environment}
    The environment for this project is a web-first system that runs on everyday devices, not special hardware. It is built for modern browsers and a Node.js-backed server, with a focus on standard open-source tools that are easy for the team to install and use.

    \begin{itemize}
        \item \textbf{Hardware:} Standard desktop or laptop computers, ideally with a current CPU, 8GB+ RAM, and internet access. No special sensors, GPUs, or physical cards are required.
        \item \textbf{Client Software:} Modern web browsers such as Chrome, Firefox, or Edge. The UI is intended for browser delivery so players can access it without installing native apps.
        \item \textbf{Server Software:} Node.js on the backend, with a typical web stack supporting REST/WebSocket communication. The team expects the backend to run in local dev environments and cloud-friendly deployments.
        \item \textbf{Data Layer:} A relational database like PostgreSQL or MySQL is expected for storing user profiles, game history, and scoring data.
        \item \textbf{Development Environment:} The code is developed with TypeScript and unit-tested using Vitest. The shared library module in `src/rev0/shared` shows this is a modern JS/TS workspace.
    \end{itemize}

    The system is a browser-based game with a Node.js backend, delivered via standard web infrastructure and accessible from ordinary notebooks or PCs.

    \section{Goals}

    {\large\bfseries Minimum Viable Product (MVP) Goals}

    \subsection{Functional Goals}
    \begin{table}[H]
        \caption{MVP Functional Goals}\label{TblMVPFunctionalGoals}
        \begin{tabular}{|p{0.22\textwidth}|p{0.46\textwidth}|p{0.28\textwidth}|}
            \hline
            \textbf{Goal} & \textbf{Description} & \textbf{Reasoning} \\
            \hline
            Core Two-Player Gameplay Loop &
            Support a 1v1 match system with turn-taking, drawing, discarding, and win checks. Includes starter card, discard pile, and reshuffling the stock pile. &
            Two players are the smallest playable unit; finishing this proves the core loop. \\
            \hline
            Classic Rules Game Engine &
            Implement standard Crazy Eights with a small twist: match by suit or rank; a ``10'' is wild and lets the player declare a suit; add another rule that incorporates counting; draw if no valid move exists. &
            Classic / flagship rules establish a solid baseline before adding notable variations. \\
            \hline
            Dozenal (Base-12) Scoring/Display &
            Display cards, scores, and numbers in Base-12 notation while keeping classic rules unchanged. &
            Introduces Dozenal in a simple way that highlights novelty while retaining accessibility. \\
            \hline
        \end{tabular}
    \end{table}

    \subsection{Non-functional Goals}
    \begin{table}[H]
        \caption{MVP Non-functional Goals}\label{TblMVPNonFunctionalGoals}
        \begin{tabular}{|p{0.22\textwidth}|p{0.46\textwidth}|p{0.28\textwidth}|}
            \hline
            \textbf{Goal} & \textbf{Description} & \textbf{Reasoning} \\
            Game Understandability &
            Simple and clear rules, Intuitive UI, and in-game prompts / notifications to guide new players. &
            Ensures the game is accessible to a wide audience, including those unfamiliar with Dozenal. \\
            \hline
            Move Validation and Feedback &
            Provide immediate invalid-move feedback, clear suit selection UI after playing a `10,'' and real-time state indicators. &
            Standardizes gameplay and behaviour; Reduces errors and learning curve; Improves usability.\\
            \hline
            Testability and Determinism &
            Support seeded shuffling and provide basic or detailed logs for each session. &
            Enables reproducible unit/integration testing and easy debugging. \\
            \hline
            Stability and Performance &
            Ensure responsive UI \(<200\,\text{ms}\), no crashes, no deadlocks, and correct reshuffling. &
            Reliability is the baseline for swift acceptance and live demonstrations. \\
            \hline
            Minimal UI &
            Provide web interface showing hand, discard pile, current state, and a Dozenal score tracker. &
            Covers essential interactions while limiting complexity at the MVP stage. \\
            \hline
            Fun gameplay &
            Ensure the game is enjoyable and engaging, with a good balance of strategy and chance. &
            A fun game will encourage players to return and learn more about Dozenal counting, increasing educational impact. \\
            \hline
        \end{tabular}
    \end{table}


    \section{Stretch Goals}

    \subsection{Functional Stretch Goals}
    \begin{table}[H]
        \caption{Functional Stretch Goals}\label{TblStretchFunctionalGoals}
        \begin{tabular}{|p{0.22\textwidth}|p{0.46\textwidth}|p{0.28\textwidth}|}
            \hline
            \textbf{Goal} & \textbf{Description} & \textbf{Reasoning} \\
            \hline
            Online Multiplayer &
            Create/join rooms and synchronize game state; provide basic reconnection. &
            Demonstrates system design capability and supports real usage. \\
            \hline
            Rule Configurator &
            Toggles for house rules (draw-until-playable, stacking eights, scoring methods in decimal or dozenal). &
            Shows variability management; supports experimentation and future product-line thinking. \\
            \hline
            Mobile-friendly UI &
            Optimize the user interface for mobile devices, ensuring touch-friendly controls and responsive design. &
            Expands the potential user base and improves accessibility across platforms. \\
            \hline
            3--4 Player Matches &
            Extend gameplay to three or more players with clear turn rotation and visualization. &
            Increases replayability; closer to common play. \\ 
            \hline
            AI Opponent &
            Computer-controlled players with simple heuristics for card choice and suit declaration. &
            Enables single-player testing and showcases extensibility. \\
            \hline
            Alternative Number Bases &
            Support additional bases (e.g. Octal, Hexadecimal) with appropriate card deck, scoring, and gameplay adjustments. &
            Demonstrates flexibility and broadens educational scope. \\
            \hline
        \end{tabular}
    \end{table}

    \subsection{Non-functional Stretch Goals}
    \begin{table}[H]
        \caption{Non-functional Stretch Goals}\label{TblStretchNonFunctionalGoals}
        \begin{tabular}{|p{0.22\textwidth}|p{0.46\textwidth}|p{0.28\textwidth}|}
            \hline
            \textbf{Goal} & \textbf{Explanation} & \textbf{Reasoning} \\
            \hline
            Tutorial and Visual Guidance &
            First-game tutorial, invalid-move highlights, and play suggestions. &
            Lowers the learning curve and improves usability. \\
            \hline
            Cross-Platform Packaging &
            Deploy as a web app or desktop executable (Windows/macOS). &
            Lowers the barrier for evaluators and external users to try the system. \\
            \hline
            Save/Replay System &
            Save completed games and replay event sequences. &
            Aids debugging, user study, and documentation. \\
            \hline
        \end{tabular}
    \end{table}

    \section{Extras}
    


    \newpage{}
    \section*{Appendix --- Reflection}

    \begin{enumerate}
        \item \textbf{What went well while writing this deliverable?} \\
        Our team collaborated effectively to define the scope of the project. We were able to clearly separate functional goals (gameplay features) and non-functional goals (quality attributes) after reviewing the lecture guidance. The use of LaTeX tables also helped us present goals in a structured and consistent format. Team communication through version control (Git) went smoothly, and everyone contributed ideas.

        \item \textbf{What pain points did you experience during this deliverable, and how did you resolve them?} \\
        One major challenge was formatting issues in LaTeX, especially with long text wrapping inside tables and ensuring that columns aligned properly. We also struggled at first with distinguishing between functional and non-functional goals, since some goals could be interpreted as both. These issues were resolved by researching LaTeX table packages, adjusting column widths, and reviewing lecture notes and examples for proper classification. Another pain point was Git conflicts during merges, which we resolved by carefully rebasing and keeping frequent communication.

        \item \textbf{How did you and your team adjust the scope of your goals to ensure they are suitable for a Capstone project (not overly ambitious but also of appropriate complexity for a senior design project)?} \\
        Initially, we considered including multiple advanced rule variants and a fully-featured online multiplayer system in the MVP. However, we realized this would be too ambitious for the timeline. Instead, we limited the MVP to a two-player local game with classic rules and base-12 scoring. More complex features, such as AI opponents and online multiplayer, were moved to the stretch goals. This adjustment ensures that the MVP is achievable while still leaving room for meaningful extensions to demonstrate complexity.

        \item \textbf{How did you handle version control and collaboration challenges?} \\
        At first, there was some confusion with branching and merging in Git. By agreeing on a workflow (feature branches merged into main through pull requests) and keeping commit messages clear, we reduced conflicts and improved traceability of changes.

        \item \textbf{How will this deliverable guide your next steps in the project?} \\
        The problem statement and goals document provides a shared roadmap for the team. It will serve as a reference point when making design decisions and prioritizing features, especially if scope adjustments are needed later in the term.
    \end{enumerate}


\end{document}