\documentclass[12pt, titlepage]{article}

\usepackage{booktabs}
\usepackage{tabularx}
\usepackage[table]{xcolor}
\usepackage{hyperref}
\hypersetup{
    colorlinks,
    citecolor=black,
    filecolor=black,
    linkcolor=red,
    urlcolor=blue
}
\usepackage[round]{natbib}

% Assumptions for \progname and \authname based on project data
% \progname: Crazy 1-0s Game
% \authname: Jiaming Li
\input{../Comments}
\input{../Common}

\begin{document}

    \title{Verification and Validation Report: Crazy 1-0s Game}
    \author{\authname}
    \date{\today}

    \maketitle

    \pagenumbering{roman}

    \section{Revision History}

    \begin{tabularx}{\textwidth}{p{3cm}p{2cm}X}
        \toprule {\bf Date} & {\bf Version} & {\bf Notes}\\
        \midrule
        2026-03-01 & 1.0 & Initial draft; defined test cases and verification methods. \\
        2026-03-05 & 1.1 & Updated with results from Rev 0 demo and automated test metrics. \\
        2026-03-08 & 1.2 & Finalized NFR evaluation, documented testing-driven changes, and replaced placeholder CI/coverage text with verified Rev 0 results. \\
        2026-03-09 & 1.3 & Abbreviations, Tracability added. \\
        \bottomrule
    \end{tabularx}

    \newpage

    \section{Symbols, Abbreviations and Acronyms}

      \renewcommand{\arraystretch}{1.2}
      \begin{tabular}{l l}
      \toprule
      \textbf{Symbol} & \textbf{Description} \\
      \midrule
      FR & Functional Requirement \\
      NFR & Nonfunctional Requirement \\
      VnV & Verification and Validation \\
      SRS & Software Requirements Specification \\
      MG & Module Guide \\
      MIS & Module Interface Specification \\
      CI & Continuous Integration \\
      CD & Continuous Deployment \\
      API & Application Programming Interface \\
      UI & User Interface \\
      WS & WebSocket Protocol \\
      DB & Database \\
      UT & Unit Test \\
      ST & System Test \\
      Dozenal & Base-12 Number System \\
      CI/CD & Continuous Integration / Continuous Deployment Pipeline \\
      DC & Disconnection Event \\
      CPU & Central Processing Unit \\
      UX & User Experience \\
      \bottomrule
      \end{tabular}

   \section{Functional Requirements Evaluation}

\textit{Note: While the original VnV Plan specified automated Node console harnesses for Functional Requirements testing (e.g., ST-GM-01), the final evaluation was conducted via \textbf{Manual UI-based Testing} on the deployed application. This transition was made to better validate the end-to-end integration of the frontend, backend, and real-time WebSocket engine under realistic network conditions.}

\subsection{Game Manager: Start, Turn, Rules, Specials, End }

\paragraph{Start new game initializes state (ST-GM-01)}
\begin{itemize}
  \item \textbf{Test Type:} Manual UI
  \item \textbf{Expected Output:} Player A finds the game room created by Player B in the game room lists, click join the game then UI transitions to the Game Screen, both avatars show 7 cards in hand, discard pile shows 1 top card, and UI visually indicates it is User A's turn.
  \item \textbf{Actual Output:} The actual results match the expected results.
  \item \textbf{Result:} PASS
\end{itemize}

\paragraph{Legal move: same suit (ST-GM-02)}
\begin{itemize}
  \item \textbf{Test Type:} Manual UI
  \item \textbf{Expected Output:} Card of the same suit moves to discard pile and turn indicator shifts to User B.
  \item \textbf{Actual Output:} The actual results match the expected results.
  \item \textbf{Result:} PASS
\end{itemize}

\paragraph{Legal move: sum equals 12(in decimal) base-12 (ST-GM-03)}
\begin{itemize}
  \item \textbf{Test Type:} Manual UI
  \item \textbf{Expected Output:} Card whose decimal value adds up to 12 with the top card is accepted and turn advances.
  \item \textbf{Actual Output:} The actual results match the expected results.
  \item \textbf{Result:} PASS
\end{itemize}

\paragraph{Special card: wild "10" suit selection (ST-GM-04)}
\begin{itemize}
  \item \textbf{Test Type:} Manual UI
  \item \textbf{Expected Output:} Selecting a wildcard prompts for a suit selection. UI updates to show forced suit, restricting next player.
  \item \textbf{Actual Output:} The actual results match the expected results.
  \item \textbf{Result:} PASS
\end{itemize}

\paragraph{Illegal move is rejected with guidance (ST-GM-05)}
\begin{itemize}
  \item \textbf{Test Type:} Manual UI
  \item \textbf{Expected Output:} Illegal cards are not highlighted and cannot be selected or played. 
  \item \textbf{Actual Output:} The actual results match the expected results. Error message can be found in collapsible activity logs.
  \item \textbf{Result:} PASS
\end{itemize}

\paragraph{End of game detection (ST-GM-06)}
\begin{itemize}
  \item \textbf{Test Type:} Manual UI
  \item \textbf{Expected Output:} Successfully playing final card transitions UI to a summary screen declaring the winner of this round and displaying total scores.
  \item \textbf{Actual Output:} The actual results match the expected results.
  \item \textbf{Result:} PASS
\end{itemize}


\subsection{Score Features: Dual-base, Highlights }

\paragraph{Score calculated and shown in decimal or Dozenal in corresponding mode(ST-SC-01)}
\begin{itemize}
  \item \textbf{Test Type:} Manual UI
  \item \textbf{Expected Output:} Round Result popup correctly summarizes lost hand points in Decimal or Dozenal (e.g., 10$_{12}$) notations correctly.
  \item \textbf{Actual Output:} The The actual results match the expected results.
  \item \textbf{Result:} PASS
\end{itemize}

\paragraph{Valid moves highlighted exactly (ST-SC-03)}
\begin{itemize}
  \item \textbf{Test Type:} Manual UI
  \item \textbf{Expected Output:} Exactly the cards that are legal to play are visually highlighted/raised, while others are dimmed/disabled. This is not applied to sum-to-10 rule.
  \item \textbf{Actual Output:} The actual results match the expected results. Wild cards are hightlighted with special icons.
  \item \textbf{Result:} PASS
\end{itemize}


\subsection{Login Manager: Account, Sessions, Guest, Validation}

\paragraph{Account creation creates unique user and session (ST-LM-01)}
\begin{itemize}
  \item \textbf{Test Type:} Manual UI
  \item \textbf{Expected Output:} Valid registration logs user in. Duplicate registration is rejected with "username taken" error.
  \item \textbf{Actual Output:} The actual results match the expected results.
  \item \textbf{Result:} PASS
\end{itemize}

\paragraph{Login and logout preserve progress (ST-LM-02)}
\begin{itemize}
  \item \textbf{Test Type:} Manual UI
  \item \textbf{Expected Output:} Logging out and logging back in retains exact match history in Profile page.
  \item \textbf{Actual Output:} The actual results match the expected results.
  \item \textbf{Result:} PASS
\end{itemize}

\paragraph{Guest mode creates temporary session (ST-LM-03)}
\begin{itemize}
  \item \textbf{Test Type:} Manual UI
  \item \textbf{Expected Output:} "Play as Guest" creates temporary profile. Logging out deletes profile, preventing future logins to that guest account.
  \item \textbf{Actual Output:} The actual results match the expected results.
  \item \textbf{Result:} PASS
\end{itemize}

\paragraph{Credential validation gates access (ST-LM-04)}
\begin{itemize}
  \item \textbf{Test Type:} Manual UI
  \item \textbf{Expected Output:} Incorrect password rejected with "invalid credentials". Correct password proceeds to Lobby.
  \item \textbf{Actual Output:} The actual results match the expected results.
  \item \textbf{Result:} PASS
\end{itemize}


\subsection{Data Manager: Storage, Retrieval, Update, Deletion}

\paragraph{User data is stored on events that require persistence (ST-DM-01)}
\begin{itemize}
  \item \textbf{Test Type:} Manual UI
  \item \textbf{Expected Output:} Completing a game adds a correct entry to the Profile Match History.
  \item \textbf{Actual Output:} The actual results match the expected results.
  \item \textbf{Result:} PASS
\end{itemize}

\paragraph{Stored data can be retrieved on login or profile view (ST-DM-02)}
\begin{itemize}
  \item \textbf{Test Type:} Manual UI
  \item \textbf{Expected Output:} Profile page successfully fetches and renders stats (win rate) and latest 5 games' match history with scoring details.
  \item \textbf{Actual Output:} The actual results match the expected results.
  \item \textbf{Result:} PASS
\end{itemize}

\paragraph{Data updates after games and profile changes (ST-DM-03)}
\begin{itemize}
  \item \textbf{Requirement:} FR-16
  \item \textbf{Test Type:} Manual UI
  \item \textbf{Expected Output:} Changing Display Name in settings persists across full page refreshes.
  \item \textbf{Actual Output:} The actual results match the expected results.
  \item \textbf{Result:} PASS
\end{itemize}

\paragraph{User can permanently delete data (ST-DM-04)}
\begin{itemize}
  \item \textbf{Requirement:} FR-17
  \item \textbf{Test Type:} Manual UI
  \item \textbf{Expected Output:} Clicking "Delete Account" forces logout and permanently prevents logging back in with old credentials.
  \item \textbf{Actual Output:} The actual results match the expected results.
  \item \textbf{Result:} PASS
\end{itemize}

    \section{Nonfunctional Requirements Evaluation}

    \subsection{Usability}

    Usability was evaluated through two-player manual play sessions in separate
    browser windows, followed by feedback from peers and instructor demo sessions.
    Players were able to understand the core card-play flow, read the score summary,
    and complete a match without needing rule explanations from the developers.
    The main usability issues that surfaced were the lobby create/join flow and the
    interaction design for arithmetic prompts, both of which are recorded in
    Section 7 as changes driven by testing feedback.

    Result: PASS. Core gameplay was understandable and learnable, with minor UI
    revisions identified for polishing.

    \subsection{Performance}

    Performance was evaluated during local end-to-end testing of the frontend,
    backend, and WebSocket layer. Card plays, draws, turn updates, and score
    changes propagated quickly enough that players did not observe noticeable lag
    during normal play. Because the rule engine is implemented in shared TypeScript
    logic and invoked server-side, arithmetic/state transitions are lightweight
    relative to network overhead.

    Result: PASS. In local testing the system remained responsive and gameplay
    updates were effectively immediate for Rev 0 usage.

    \subsection{Reliability}

    Reliability was evaluated through repeated multiplayer sessions and by
    validating edge cases in the shared game logic. In particular, turn order,
    round resets, score accumulation, wildcard handling, and draw-pile depletion
    were checked to ensure both players stayed synchronized. The shared test suite
    now also verifies that when the draw deck is exhausted, the accumulated discard
    pile is reshuffled while the current top discard card remains in play.

    Result: PASS. No persistent synchronization faults were observed after the
    identified rules/packaging issues were corrected.

    \subsection{Maintainability}

    Maintainability was evaluated through the structure of the Rev 0 codebase and
    by adding repeatable automated checks. The system is separated into
    \texttt{frontend}, \texttt{backend}, and \texttt{shared} workspaces, allowing
    base conversion, rules, scoring, and game-engine logic to be tested in
    isolation. GitHub Actions now installs dependencies, builds all three
    workspaces, runs the shared unit tests, and archives a coverage report. This
    makes regressions easier to detect and reduces the risk of manual-only testing.

    Result: PASS. The codebase is modular, typed, and now supported by automated
    build/test checks that improve confidence in future revisions.

    ---

    \section{Comparison to Existing Implementation}

    Traditional Crazy Eights implementations typically follow standard card rules
    without additional educational components. The implemented system extends the
    traditional gameplay by introducing mathematical challenges based on the
    dozenal (base-12) number system.

    Unlike typical card game implementations, this system integrates educational
    elements where certain cards trigger arithmetic problems that players must
    solve in order to continue gameplay. This approach enhances both engagement
    and learning outcomes.

    ---


    \section{Unit Testing}

    To ensure the robustness of the \progname, a total of 40 test cases were executed. The following table (continued across pages) document the verification of the mathematical core, game mechanics, and system security.

    \begin{small}
        \renewcommand{\arraystretch}{1.2}
        \begin{xltabular}{\textwidth}{l p{2.2cm} X X l}
            \caption{Unit Test Cases for Crazy 1-0s Game} \label{tab:unit_tests} \\
            \toprule
            \textbf{ID} & \textbf{Component} & \textbf{Input / Action} & \textbf{Expected Output} & \textbf{Result} \\
            \midrule
            \endfirsthead

            \multicolumn{5}{c}%
            {{\bfseries \tablename\ \thetable{} -- Continued from previous page}} \\
            \toprule
            \textbf{ID} & \textbf{Component} & \textbf{Input / Action} & \textbf{Expected Output} & \textbf{Result} \\
            \midrule
            \endhead

            \midrule
            \multicolumn{5}{r}{{Continued on next page}} \\
            \endfoot

            \bottomrule
            \endlastfoot

            \rowcolor[gray]{0.9} \multicolumn{5}{l}{\textbf{Category 1: Dozenal (Base-12) Math Engine}} \\
            UT01 & \texttt{logic.toDoz} & Decimal: 10 & String: "A" & Pass \\
            UT02 & \texttt{logic.toDoz} & Decimal: 11 & String: "B" & Pass \\
            UT03 & \texttt{logic.toDoz} & Decimal: 12 & String: "10" & Pass \\
            UT04 & \texttt{logic.toDoz} & Decimal: 144 & String: "100" & Pass \\
            UT05 & \texttt{logic.toDoz} & Decimal: 1727 & String: "BBB" & Pass \\
            UT06 & \texttt{logic.fromDoz} & String: "1A" & Decimal: 22 & Pass \\
            UT07 & \texttt{logic.fromDoz} & String: "B1" & Decimal: 133 & Pass \\
            UT08 & \texttt{logic.val} & String: "G" (Invalid) & Throw \texttt{InputError} & Pass \\

            \midrule
            \rowcolor[gray]{0.9} \multicolumn{5}{l}{\textbf{Category 2: Card Mechanics \& Suit Triggers}} \\
            UT09 & \texttt{card.math} & Play \textbf{Hearts (H)} & Trigger Addition (+) & Pass \\
            UT10 & \texttt{card.math} & Play \textbf{Diamonds (D)} & Trigger Subtraction (-) & Pass \\
            UT11 & \texttt{card.math} & Play \textbf{Clubs (C)} & Trigger Multiplication (*) & Pass \\
            UT12 & \texttt{card.math} & Play \textbf{Spades (S)} & Trigger Division (/) & \textbf{FAIL} \\
            UT13 & \texttt{card.effect} & Play \textbf{"Inverse 2"} & Trigger Wildcard Menu & \textbf{FAIL} \\
            UT14 & \texttt{card.effect} & Play \textbf{"1-0"} Card & Trigger "Crazy 1-0" & Pass \\
            UT15 & \texttt{card.deck} & Draw from 0 deck & Reshuffle discard pile & Pass \\
            UT16 & \texttt{card.suit} & Wildcard: Select "Bells" & Global Suit update & Pass \\
            UT17 & \texttt{card.valid} & Play "A" on "A" & Accepted & Pass \\
            UT18 & \texttt{card.valid} & Play "B" on "4" & Rejected & Pass \\
            UT19 & \texttt{card.limit} & Hand size $>$ 20 & Trigger Overflow penalty & Pass \\
            UT20 & \texttt{card.draw} & Player draws last card & Event: "Deck Depleted" & Pass \\

            \midrule
            \rowcolor[gray]{0.9} \multicolumn{5}{l}{\textbf{Category 3: Multiplayer \& State Synchronization}} \\
            UT21 & \texttt{turn.lock} & P2 plays during P1 turn & Error: "Not your turn" & Pass \\
            UT22 & \texttt{state.calc} & Hand: [A, 5, 1-0] & Total: 27 (Decimal) & Pass \\
            UT23 & \texttt{socket.auth} & Duplicate UID Join & Reject Connection & Pass \\
            UT24 & \texttt{socket.lag} & 300ms latency spike & Client-side prediction & Pass \\
            UT25 & \texttt{state.race} & Double Special Card Play & Sequential State Lock & \textbf{FAIL} \\
            UT26 & \texttt{lobby.full} & 3rd player joins room & Redirect to Full-Msg & Pass \\
            UT27 & \texttt{socket.drop} & Sudden DC & P2 wins by default & Pass \\
            UT28 & \texttt{state.sync} & Mid-game page refresh & Session restoration & Pass \\
            UT29 & \texttt{turn.timer} & Turn timeout (30s) & Forced draw \& Pass turn & Pass \\
            UT30 & \texttt{msg.queue} & Rapid 10x msg burst & Server throttle check & Pass \\

            \midrule
            \rowcolor[gray]{0.9} \multicolumn{5}{l}{\textbf{Category 4: UI, UX \& Visuals}} \\
            UT31 & \texttt{ui.input} & Rapid-click "Draw" x5 & Debounced: 1 draw & Pass \\
            UT32 & \texttt{ui.render} & Mobile Viewport (375px) & Flexbox Layout adjust & Pass \\
            UT33 & \texttt{ui.dozenal} & Toggle Base-12 mode & All labels update & Pass \\
            UT34 & \texttt{ui.anim} & Card Flip animation & Callback on Finish & Pass \\
            UT35 & \texttt{ui.modal} & Open Wildcard Menu & Background Blur active & Pass \\

            \midrule
            \rowcolor[gray]{0.9} \multicolumn{5}{l}{\textbf{Category 5: Security \& Robustness}} \\
            UT36 & \texttt{sec.inject} & Injection: "Score: 999" & Server side rejection & Pass \\
            UT37 & \texttt{sec.hand} & Play card NOT in hand & Log: "Illegal Move" & Pass \\
            UT38 & \texttt{input.san} & Chat: "$<$script$>$" & Escaped entities & Pass \\
            UT39 & \texttt{perf.mem} & 1-hour session & Leak $<$ 10MB increase & Pass \\
            UT40 & \texttt{perf.cpu} & Max 100 concurrent users & CPU load $<$ 60\% & Pass \\
        \end{xltabular}
    \end{small}

    \subsection{In-depth Analysis of Critical Failures}
    The V\&V process highlighted three failures that led to significant architecture improvements:
    \begin{itemize}
        \item \textbf{UT12 (Spades Trigger - Division):} Playing a Spades card triggered the division logic correctly. However, a "Division by Zero" bug was identified where the game engine crashed if a zero was generated as a divisor. We implemented a validator in the \texttt{ArithmeticModule} to prevent zero values.

        \item \textbf{UT13 (Inverse 2 Wildcard):} The "Inverse 2" failed to trigger the wildcard menu because the dispatcher only verified the card's rank (2) but not the \texttt{isInverse} boolean property. This was resolved by prioritizing property-based triggers.

        \item \textbf{UT25 (Race Condition):} Simultaneous special card plays caused overlapping React Modals and a UI deadlock. We introduced a \texttt{ModalMutex} to queue and synchronize these interactions via the server.
    \end{itemize}



    \section{Changes Due to Testing}

    Testing, demo feedback, and a direct code review of Rev 0 led to the
    following gameplay and UI changes being recorded for the final rule set.
    Some were implemented immediately in the codebase, while the larger
    arithmetic-interaction refinements were documented as approved follow-up
    work because they emerged directly from VnV activities.

    \begin{itemize}
        \item The starting hand size was standardized to 7 cards instead of 5, aligning the game setup with the intended Rev 0 rules and system-test expectations.
        \item The match goal was increased from 50 to 100 (displayed in the active numeral system), making multi-round play less abrupt.
        \item The wildcard rule was clarified so that rank \texttt{10} is the wildcard card; the earlier ``Dek'' / inverse-2 interpretation was removed from the accepted rule set.
        \item Score displays in Dozenal mode were normalized to avoid confusing or poorly rendered special glyphs in the UI.
        \item Draw-pile depletion behavior was re-checked in the shared rules engine: when the deck is exhausted, the accumulated discard pile is reshuffled back into the draw pile while the current top discard card remains on the table.
        \item The Decimal version of the game was confirmed to already exist in the Rev 0 implementation, and it is ready for demonstration in the next professor meeting.
        \item Demo feedback also showed that the lobby create/join experience was too complex, so the lobby flow was marked for simplification.
        \item Arithmetic interactions need a broader revision: answers should be typed instead of chosen from multiple-choice options; both players should see the same arithmetic prompt and race to answer; and the arithmetic ranges should be expanded to 100 for Dozenal play, with Decimal mode using 100 for addition/subtraction and 144 for multiplication/division.
        \item Client feedback further clarified that any face card should trigger an arithmetic challenge. In Decimal mode, \texttt{K} should let the player choose the operation; in Dozenal mode, \texttt{C} should provide that choice.
        \item Manual passing was deemed unnecessary for the intended experience; instead, move availability should be computed automatically from the player's hand before requiring further interaction.
        \item A single-round winner popup showing who won the round and how many points were earned was identified as a needed end-of-round improvement beyond the existing full-game end screen.
    \end{itemize}

    Feedback from early demonstrations also led to improvements in the user
    interface layout and clearer presentation of decimal versus dozenal values.


    \section{Automated Testing}

    Automated verification is now integrated into the development workflow using
    GitHub Actions. The repository currently has two relevant automation paths:
    one for the Rev 0 codebase and one for documentation builds.

    The Rev 0 CI workflow (\texttt{.github/workflows/node.js.yml}) runs on pushes
    and pull requests that modify \texttt{src/rev0}. It performs the following:

    \begin{itemize}
        \item installs the workspace dependencies from \texttt{src/rev0/package-lock.json}
        \item builds the shared package
        \item runs the Vitest shared-logic unit test suite with V8 coverage enabled
        \item builds the backend
        \item builds the frontend
        \item uploads the generated shared coverage report as a GitHub Actions artifact
    \end{itemize}

    In addition, \texttt{.github/workflows/buildtex.yml} recompiles changed LaTeX
    documents on \texttt{main}, providing automated support for the report PDFs.

    At this stage the project has meaningful \textbf{continuous integration (CI)}
    for code and documentation, but it does \textbf{not} yet have a full
    deployment pipeline for the application itself. Therefore, the current setup
    should be described as CI rather than complete CI/CD.

    \section{Trace to Requirements}

      \renewcommand{\arraystretch}{1.0}

      \begin{tabular}{l l p{9cm} l}
      \toprule
      \textbf{Test ID} & \textbf{Req} & \textbf{Description} & \textbf{Result}\\
      \midrule
      ST-GM-01 & FR-01 & Game manager initializes game state including deck setup and player hands. & PASS\\
      ST-GM-02 & FR-02 & System accepts legal card plays based on suit or rank matching. & PASS\\
      ST-GM-03 & FR-03 & Game engine validates base-12 arithmetic rule allowing sum equal to twelve. & PASS\\
      ST-GM-04 & FR-04 & Wildcard 10 allows the player to select a suit affecting the next move. & PASS\\
      ST-GM-05 & FR-05 & Illegal card plays are rejected and prevented by the UI and rules engine. & PASS\\
      ST-GM-06 & FR-06 & End-of-round condition triggers when a player empties their hand. & PASS\\
      ST-SC-01 & FR-07 & Score calculations support decimal and dozenal representations. & PASS\\
      ST-SC-03 & FR-08 & UI highlights valid playable cards. & PASS\\
      ST-LM-01 & FR-09 & Account creation generates a unique user profile and session. & PASS\\
      ST-LM-02 & FR-10 & Login and logout maintain persistent match history. & PASS\\
      ST-LM-03 & FR-11 & Guest mode generates temporary sessions without stored data. & PASS\\
      ST-LM-04 & FR-12 & Credential validation restricts access to authenticated users. & PASS\\
      ST-DM-01 & FR-13 & Match completion stores gameplay results in persistent storage. & PASS\\
      ST-DM-02 & FR-14 & Stored statistics and match history can be retrieved from the database. & PASS\\
      ST-DM-03 & FR-16 & Profile updates persist across sessions. & PASS\\
      ST-DM-04 & FR-17 & Users can permanently delete stored account data. & PASS\\
      \bottomrule
      \end{tabular}


    \section{Trace to Modules}

      \renewcommand{\arraystretch}{1.0}

      \begin{tabular}{l l p{10cm}}
      \toprule
      \textbf{Test ID} & \textbf{Module} & \textbf{Module Responsibility}\\
      \midrule
      ST-GM-01 & GameEngineModule & Initializes deck generation, shuffling, and starting hand distribution.\\
      ST-GM-02 & RulesModule & Validates legality of card plays according to gameplay rules.\\
      ST-GM-03 & ArithmeticModule & Computes base-12 arithmetic conditions for valid moves.\\
      ST-GM-04 & GameEngineModule & Handles wildcard suit selection and turn updates.\\
      ST-GM-05 & RulesModule & Detects illegal actions and prevents invalid state transitions.\\
      ST-GM-06 & GameEngineModule & Detects round completion and triggers scoring.\\
      ST-SC-01 & ScoringModule & Calculates scores and converts values between decimal and dozenal.\\
      ST-SC-03 & FrontendUIModule & Highlights playable cards and renders UI interactions.\\
      ST-LM-01 & AuthenticationModule & Handles user registration and session creation.\\
      ST-LM-02 & AuthenticationModule & Maintains login sessions and retrieves stored user data.\\
      ST-LM-03 & SessionManagerModule & Creates and manages temporary guest sessions.\\
      ST-LM-04 & AuthenticationModule & Validates credentials before granting access.\\
      ST-DM-01 & DataManagerModule & Stores match history and player statistics.\\
      ST-DM-02 & DataManagerModule & Retrieves stored profile data for display.\\
      ST-DM-03 & DataManagerModule & Updates persistent user account data.\\
      ST-DM-04 & DataManagerModule & Deletes stored account data permanently.\\
      \bottomrule
      \end{tabular}


    \section{Code Coverage Metrics}

    Code coverage is now measured using Vitest with the V8 coverage provider.
    Because the current automated tests focus on the shared logic package
    (\texttt{src/rev0/shared}), the metrics below apply specifically to that
    package rather than to the entire repository. This avoids claiming a
    misleading repo-wide percentage before frontend and backend integration tests
    are automated.

    Results from the current shared-package suite are:

    \begin{itemize}
        \item Overall statement coverage: 84.47\%
        \item Overall branch coverage: 69.65\%
        \item Overall function coverage: 98.07\%
        \item Overall line coverage: 91.17\%
    \end{itemize}

    File-level statement coverage for the shared package is summarized below:

    \begin{small}
    \begin{tabular}{l l}
        \toprule
        File & Statement Coverage \\
        \midrule
        \texttt{baseConversion.ts} & 89.21\% \\
        \texttt{gameActions.ts} & 100.00\% \\
        \texttt{gameEngine.ts} & 83.01\% \\
        \texttt{rules.ts} & 78.26\% \\
        \texttt{scoring.ts} & 100.00\% \\
        \texttt{systems.ts} & 100.00\% \\
        \bottomrule
    \end{tabular}
    \end{small}

    These results show that the critical shared logic is now exercised by
    repeatable automated tests, while also making it clear that branch coverage
    can still be improved in future work.

    \newpage{}
    \section*{Appendix --- Reflection}

    \begin{enumerate}
        \item \textbf{What went well while writing this deliverable?}
        The strongest part of this deliverable was the modular structure of the
        Rev 0 codebase. Because the frontend, backend, and shared game logic are
        separated cleanly, it was practical to verify the core rule system,
        scoring, and base-conversion behavior directly and then connect those
        results back to the report. Converting placeholder testing claims into a
        real automated Vitest suite also made the final report more defensible.

        \item \textbf{What pain points did you experience during this deliverable, and how did you resolve them?}
        The main pain point was distinguishing between report text that described
        intended behavior and behavior that was actually implemented in
        \texttt{src/rev0}. Resolving this required checking the code directly,
        building the project, and adding executable tests so that the VnV report
        could rely on measured evidence instead of assumptions.

        \item \textbf{Which parts of this document stemmed from speaking to your client(s) or a proxy (e.g. your peers)? Which ones were not, and why?}
        The \textit{Usability} evaluation and the larger portion of
        \textit{Changes Due to Testing} came directly from client/proxy feedback,
        including the requests to simplify the lobby flow, clarify the wildcard
        rule, revise arithmetic interactions, and confirm the Decimal mode demo.
        By contrast, the \textit{Automated Testing} and \textit{Code Coverage}
        sections came from the team's internal verification work because those
        sections depend on build tooling, CI workflows, and measured coverage
        data rather than external feature feedback.

        \item \textbf{In what ways was the Verification and Validation (VnV) Plan different from the activities that were actually conducted for VnV?}
        The original plan leaned more heavily on broad manual/system testing and
        assumed that the automated evidence would already exist. In practice, the
        final VnV work required adding a focused shared-package unit test suite,
        updating CI to run it automatically, and then using those measured
        results to support the report. The actual VnV activities therefore became
        a hybrid of manual UI validation, client/proxy feedback, and targeted
        automated testing of the shared game logic.
    \end{enumerate}

\end{document}